# This code was used manipulate data from the raw data output from Genemarker to the input data file for GenAlex.

## Set working directory
setwd("C:/Users/Sara/Documents/EEB_2016-2018/Peak tables/Intermediate_files")


## Packages
```{r}
if (!require("readr")) install.packages("readr")
library(readr)

if (!require("reshape2")) install.packages("reshape2")
library(reshape2)

if (!require("dplyr")) install.packages("dplyr")
library(dplyr)

if (!require("gsubfn")) install.packages("gsubfn")
library(gsubfn)

if (!require("stringr")) install.packages("stringr")
library(stringr)

if (!require("tidyr")) install.packages("tidyr")
library(tidyr)
```

# Converting raw data from Genemarker into complete dataset by locus

## A103
```{r}
A103_raw <- read.table("A103_raw.csv", sep = ",", na.strings = c("", "NA"))
A103 <- A103_raw[,-c(2:6)] #cut out unnecessary columns
A103 <- A103[,-c(3:8)] #cut out unnecessary columns
names(A103) <- c("Sample_ID", "A103") #rename columns
A103[A103 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A103 = A103 %>% na.omit() #omit all NAs
A103$Sample_ID <- str_sub(A103$Sample, 5, 17) #Remove lane name and underscore
A103$Sample_ID <- strapplyc(A103$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A103 <- A103[order(A103$Sample_ID),]

View(A103)
```

## A115
```{r}
A115_raw <- read.table("A115_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A115 <- A115_raw[,-c(2:6)] #cut out unnecessary columns
A115 <- A115[,-c(3:8)] #cut out unnecessary columns
names(A115) <- c("Sample_ID", "A115") #rename columns
A115[A115 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A115 = A115 %>% na.omit() #omit NAs again
A115$Sample_ID <- str_sub(A115$Sample, 5, 18) #Remove lane name and underscore
A115$Sample_ID <- strapplyc(A115$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
A115 <- A115[order(A115$Sample_ID),]
View(A115)
```


## A120
```{r}
A120_raw <- read.table("A120_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A120 <- A120_raw[,-c(2:6)] #cut out unnecessary columns
A120 <- A120[,-c(3:8)] #cut out unnecessary columns
names(A120) <- c("Sample_ID", "A120") #rename columns
A120[A120 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A120 = A120 %>% na.omit() #omit NAs again
A120$Sample_ID <- str_sub(A120$Sample, 5, 18) #Remove lane name and underscore
A120$Sample_ID <- strapplyc(A120$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A120 <- A120[order(A120$Sample_ID),]

View(A120)
```


## C1
```{r}
C1_raw <- read.table("C1_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C1 <- C1_raw[,-c(2:6)] #cut out unnecessary columns
C1 <- C1[,-c(3:8)] #cut out unnecessary columns
names(C1) <- c("Sample_ID", "C1") #rename columns
C1[C1 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C1 = C1 %>% na.omit() #omit NAs again
C1$Sample_ID <- str_sub(C1$Sample, 5, 18) #Remove lane name and underscore
C1$Sample_ID <- strapplyc(C1$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C1 <- C1[order(C1$Sample_ID),]

View(C1)
```


## C6
```{r}
C6_raw <- read.table("C6_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C6 <- C6_raw[,-c(2:6)] #cut out unnecessary columns
C6 <- C6[,-c(3:8)] #cut out unnecessary columns
names(C6) <- c("Sample_ID", "C6") #rename columns
C6[C6 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C6 = C6 %>% na.omit() #omit NAs again
C6$Sample_ID <- str_sub(C6$Sample, 5, 18) #Remove lane name and underscore
C6$Sample_ID <- strapplyc(C6$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C6 <- C6[order(C6$Sample_ID),]

View(C6)
```


## C105
```{r}
C105_raw <- read.table("C105_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C105 <- C105_raw[,-c(2:6)] #cut out unnecessary columns
C105 <- C105[,-c(3:8)] #cut out unnecessary columns
names(C105) <- c("Sample_ID", "C105") #rename columns
C105[C105 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C105 = C105 %>% na.omit() #omit NAs again
C105$Sample_ID <- str_sub(C105$Sample, 5, 18) #Remove lane name and underscore
C105$Sample_ID <- strapplyc(C105$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C105 <- C105[order(C105$Sample_ID),]

View(C105)
```


## C125
```{r}
C125_raw <- read.table("C125_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C125 <- C125_raw[,-c(2:6)] #cut out unnecessary columns
C125 <- C125[,-c(3:8)] #cut out unnecessary columns
names(C125) <- c("Sample_ID", "C125") #rename columns
C125[C125 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C125 = C125 %>% na.omit() #omit NAs again
C125$Sample_ID <- str_sub(C125$Sample, 5, 18) #Remove lane name and underscore
C125$Sample_ID <- strapplyc(C125$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C125 <- C125[order(C125$Sample_ID),]

View(C125)
```


## D4
```{r}
D4_raw <- read.table("D4_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D4 <- D4_raw[,-c(2:6)] #cut out unnecessary columns
D4 <- D4[,-c(3:8)] #cut out unnecessary columns
names(D4) <- c("Sample_ID", "D4") #rename columns
D4[D4 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D4 = D4 %>% na.omit() #omit NAs again
D4$Sample_ID <- str_sub(D4$Sample, 5, 18) #Remove lane name and underscore
D4$Sample_ID <- strapplyc(D4$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D4 <- D4[order(D4$Sample_ID),]

View(D4)
```


## D10
```{r}
D10_raw <- read.table("D10_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D10 <- D10_raw[,-c(2:6)] #cut out unnecessary columns
D10 <- D10[,-c(3:8)] #cut out unnecessary columns
names(D10) <- c("Sample_ID", "D10") #rename columns
D10[D10 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D10 = D10 %>% na.omit() #omit NAs again
D10$Sample_ID <- str_sub(D10$Sample, 5, 18) #Remove lane name and underscore
D10$Sample_ID <- strapplyc(D10$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D10 <- D10[order(D10$Sample_ID),]

View(D10)
```


## D106
```{r}
D106_raw <- read.table("D106_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D106 <- D106_raw[,-c(2:6)] #cut out unnecessary columns
D106 <- D106[,-c(3:8)] #cut out unnecessary columns
names(D106) <- c("Sample_ID", "D106") #rename columns
D106[D106 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D106 = D106 %>% na.omit() #omit NAs again
D106$Sample_ID <- str_sub(D106$Sample, 5, 18) #Remove lane name and underscore
D106$Sample_ID <- strapplyc(D106$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D106 <- D106[order(D106$Sample_ID),]

View(D106)
```


## D113
```{r}
D113_raw <- read.table("D113_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D113 <- D113_raw[,-c(2:6)] #cut out unnecessary columns
D113 <- D113[,-c(3:8)] #cut out unnecessary columns
names(D113) <- c("Sample_ID", "D113") #rename columns
D113[D113 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D113 = D113 %>% na.omit() #omit NAs again
D113$Sample_ID <- str_sub(D113$Sample, 5, 18) #Remove lane name and underscore
D113$Sample_ID <- strapplyc(D113$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D113 <- D113[order(D113$Sample_ID),]

View(D113)
```

## D114
```{r}
D114_raw <- read.table("D114_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D114 <- D114_raw[,-c(2:6)] #cut out unnecessary columns
D114 <- D114[,-c(3:8)] #cut out unnecessary columns
names(D114) <- c("Sample_ID", "D114") #rename columns
D114[D114 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D114 = D114 %>% na.omit() #omit NAs again
D114$Sample_ID <- str_sub(D114$Sample, 5, 18) #Remove lane name and underscore
D114$Sample_ID <- strapplyc(D114$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D114 <- D114[order(D114$Sample_ID),]

View(D114)
```

## D119
```{r}
D119_raw <- read.table("D119_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D119 <- D119_raw[,-c(2:6)] #cut out unnecessary columns
D119 <- D119[,-c(3:8)] #cut out unnecessary columns
names(D119) <- c("Sample_ID", "D119") #rename columns
D119[D119 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D119 = D119 %>% na.omit() #omit NAs again
D119$Sample_ID <- str_sub(D119$Sample, 5, 18) #Remove lane name and underscore
D119$Sample_ID <- strapplyc(D119$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D119 <- D119[order(D119$Sample_ID),]

View(D119)
```


## D125
```{r}
D125_raw <- read.table("D125_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D125 <- D125_raw[,-c(2:6)] #cut out unnecessary columns
D125 <- D125[,-c(3:8)] #cut out unnecessary columns
names(D125) <- c("Sample_ID", "D125") #rename columns
D125[D125 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D125 = D125 %>% na.omit() #omit NAs again
D125$Sample_ID <- str_sub(D125$Sample, 5, 18) #Remove lane name and underscore
D125$Sample_ID <- strapplyc(D125$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D125 <- D125[order(D125$Sample_ID),]

View(D125)
```

# Converting data from Genemarker for 12 Wisconsin samples

## A103 
```{r}
A103_wisraw <- read.table("A103_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A103_wis <- A103_wisraw[,-c(2:6)] #cut out unnecessary columns
A103_wis <- A103_wis[,-c(3:8)] #cut out unnecessary columns
names(A103_wis) <- c("Sample_ID", "A103") #rename columns
A103_wis[A103_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
A103_wis[A103_wis == "OL"] <- NA #convert sample to NAs so they can be omitted
A103_wis = A103_wis %>% na.omit() #omit NAs again
A103_wis$Sample_ID <- str_sub(A103_wis$Sample, 5, 17) #Remove lane name and underscore
A103_wis$Sample_ID <- strapplyc(A103_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
A103_wis <- A103_wis[order(A103_wis$Sample_ID),]

View(A103_wis)
```


## A120
```{r}
A120_wisraw <- read.table("A120_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A120_wis <- A120_wisraw[,-c(2:6)] #cut out unnecessary columns
A120_wis <- A120_wis[,-c(3:8)] #cut out unnecessary columns
names(A120_wis) <- c("Sample_ID", "A120") #rename columns
A120_wis[A120_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
A120_wis = A120_wis %>% na.omit() #omit NAs again
A120_wis$Sample_ID <- str_sub(A120_wis$Sample, 5, 18) #Remove lane name and underscore
A120_wis$Sample_ID <- strapplyc(A120_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A120_wis <- A120_wis[order(A120_wis$Sample_ID),]

View(A120_wis)
```


## C1
```{r}
C1_wisraw <- read.table("C1_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C1_wis <- C1_wisraw[,-c(2:5)] #cut out unnecessary columns
C1_wis <- C1_wis[,-c(4:8)] #cut out unnecessary columns
names(C1_wis) <- c("Sample_ID", "C1") #rename columns
C1_wis[C1_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C1_wis = C1_wis %>% na.omit() #omit all NAs
C1_wis$Sample_ID <- str_sub(C1_wis$Sample, 5, 18) #Remove lane name and underscore
C1_wis$Sample_ID <- strapplyc(C1_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C1_wis <- C1_wis[order(C1_wis$Sample_ID),]

View(C1_wis)
```


## C6
```{r}
C6_wisraw <- read.table("C6_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C6_wis <- C6_wisraw[,-c(2:6)] #cut out unnecessary columns
C6_wis <- C6_wis[,-c(3:8)] #cut out unnecessary columns
names(C6_wis) <- c("Sample_ID", "C6") #rename columns
C6_wis[C6_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C6_wis = C6_wis %>% na.omit() #omit NAs again
C6_wis$Sample_ID <- str_sub(C6_wis$Sample, 5, 18) #Remove lane name and underscore
C6_wis$Sample_ID <- strapplyc(C6_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C6_wis <- C6_wis[order(C6_wis$Sample_ID),]

View(C6_wis)
```


## C105
```{r}
C105_wisraw <- read.table("C105_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C105_wis <- C105_wisraw[,-c(2:6)] #cut out unnecessary columns
C105_wis <- C105_wis[,-c(3:8)] #cut out unnecessary columns
names(C105_wis) <- c("Sample_ID", "C105") #rename columns
C105_wis[C105_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C105_wis = C105_wis %>% na.omit() #omit NAs again
C105_wis$Sample_ID <- str_sub(C105_wis$Sample, 5, 18) #Remove lane name and underscore
C105_wis$Sample_ID <- strapplyc(C105_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C105_wis <- C105_wis[order(C105_wis$Sample_ID),]

View(C105_wis)
```


## D4
```{r}
D4_wisraw <- read.table("D4_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D4_wis <- D4_wisraw[,-c(2:6)] #cut out unnecessary columns
D4_wis <- D4_wis[,-c(3:8)] #cut out unnecessary columns
names(D4_wis) <- c("Sample_ID", "D4") #rename columns
D4_wis[D4_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D4_wis = D4_wis %>% na.omit() #omit all NAs
D4_wis$Sample_ID <- str_sub(D4_wis$Sample, 5, 18) #Remove lane name and underscore
D4_wis$Sample_ID <- strapplyc(D4_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D4_wis <- D4_wis[order(D4_wis$Sample_ID),]

View(D4_wis)
```


## D10
```{r}
D10_wisraw <- read.table("D10_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D10_wis <- D10_wisraw[,-c(2:6)] #cut out unnecessary columns
D10_wis <- D10_wis[,-c(3:8)] #cut out unnecessary columns
names(D10_wis) <- c("Sample_ID", "D10") #rename columns
D10_wis[D10_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D10_wis = D10_wis %>% na.omit() #omit NAs again
D10_wis$Sample_ID <- str_sub(D10_wis$Sample, 5, 18) #Remove lane name and underscore
D10_wis$Sample_ID <- strapplyc(D10_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D10_wis <- D10_wis[order(D10_wis$Sample_ID),]

View(D10_wis)
```


## D106
```{r}
D106_wisraw <- read.table("D106_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D106_wis <- D106_wisraw[,-c(2:6)] #cut out unnecessary columns
D106_wis <- D106_wis[,-c(3:8)] #cut out unnecessary columns
names(D106_wis) <- c("Sample_ID", "D106") #rename columns
D106_wis[D106_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D106_wis = D106_wis %>% na.omit() #omit NAs again
D106_wis$Sample_ID <- str_sub(D106_wis$Sample, 5, 18) #Remove lane name and underscore
D106_wis$Sample_ID <- strapplyc(D106_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D106_wis <- D106_wis[order(D106_wis$Sample_ID),]

View(D106_wis)
```



# Merge loci genotypes together and edit data
```{r}
# Merge genos of a few and edit before adding more
genos <- merge(A103, A115, all= T, sort=T) 
genos <- merge(genos, A120, by="Sample_ID", all=T)
genos <- merge(genos, C1, by="Sample_ID", all=T)
genos <- merge(genos, C6, by="Sample_ID", all=T)
genos <- merge(genos, C105, by="Sample_ID", all=T)
genos <- merge(genos, C125, by="Sample_ID", all=T)
# Remove duplicates
genos1 <- genos[duplicated(genos,)]
genos <- merge(genos, D4, by="Sample_ID", all=T)
genos <- merge(genos, D10, by="Sample_ID", all=T)
genos <- merge(genos, D106, by="Sample_ID", all=T)
genos <- merge(genos, D113, by="Sample_ID", all=T)
genos <- merge(genos, D114, by="Sample_ID", all=T)
genos <- merge(genos, D119, by="Sample_ID", all=T)
genos <- merge(genos, D125, by="Sample_ID", all=T)

#genos <- merge(genos, A103_wis, by="Sample_ID", all=T)
#genos <- merge(genos, A120_wis, by="Sample_ID", all=T)
#genos <- merge(genos, C1_wis, by="Sample_ID", all=T)
#genos <- merge(genos, C6_wis, by="Sample_ID", all=T)
#genos <- merge(genos, C105_wis, by="Sample_ID", all=T)
#genos <- merge(genos, D4_wis, by="Sample_ID", all=T)
#genos <- merge(genos, D10_wis, by="Sample_ID", all=T)
#genos <- merge(genos, D106_wis, by="Sample_ID", all=T)

View(genos)
#genos[is.na(genos)] <- 0

```

# Add duplicate row for second homozygous allele and spread data
```{r}
# Must be done at each locus
# A103 locus
A103[(nrow(A103)+1),] <- c("ALL3", "244")
A103[(nrow(A103)+1),] <- c("ALL10", "242")
A103[(nrow(A103)+1),] <- c("ALL11", "242")
A103[(nrow(A103)+1),] <- c("ALL4", "242")
A103[(nrow(A103)+1),] <- c("ALL7", "244")
A103[(nrow(A103)+1),] <- c("BEF-07212-01", "244")
A103[(nrow(A103)+1),] <- c("C041", "251")
A103[(nrow(A103)+1),] <- c("INHS-25558", "246")
A103[(nrow(A103)+1),] <- c("m-07-07", "257")
A103[(nrow(A103)+1),] <- c("MS33", "244")
A103[(nrow(A103)+1),] <- c("MS36", "249")
A103[(nrow(A103)+1),] <- c("Pcyph-TN-2", "240")
A103[(nrow(A103)+1),] <- c("PMC-8", "249")
A103 <- A103[order(A103$Sample_ID),]
# Remove Chip 5 OL call
A103 <- A103[-c(94),]
# Remove INHS-16244 duplicate
A103 <- A103[-c(129),]
# Replace incorrect Sample_IDs
A103$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A103$Sample_ID)
# Spread data
#dummy <- c("high", "low")
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# A115 locus
A115[(nrow(A115)+1),] <- c("130-3", "310")
A115[(nrow(A115)+1),] <- c("237-1", "301")
A115[(nrow(A115)+1),] <- c("C024", "301")
A115[(nrow(A115)+1),] <- c("Chip-04", "292")
A115[(nrow(A115)+1),] <- c("Chip-10", "303")
A115[(nrow(A115)+1),] <- c("Chip-14", "310")
A115[(nrow(A115)+1),] <- c("Chip6_537304", "285")
A115[(nrow(A115)+1),] <- c("m-07-05", "292")
A115[(nrow(A115)+1),] <- c("Meramec-A", "292")
A115[(nrow(A115)+1),] <- c("Meramec-B", "285")
A115[(nrow(A115)+1),] <- c("MS17", "299")
A115[(nrow(A115)+1),] <- c("MS2", "301")
A115[(nrow(A115)+1),] <- c("MS20", "301")
A115[(nrow(A115)+1),] <- c("MS22", "285")
A115[(nrow(A115)+1),] <- c("MS23", "285")
A115[(nrow(A115)+1),] <- c("MS25", "292")
A115[(nrow(A115)+1),] <- c("MS27", "292")
A115[(nrow(A115)+1),] <- c("MS28", "299")
A115[(nrow(A115)+1),] <- c("MS3", "285")
A115[(nrow(A115)+1),] <- c("MS37", "301")
A115[(nrow(A115)+1),] <- c("MS23", "285")
A115[(nrow(A115)+1),] <- c("MS39", "292")
A115[(nrow(A115)+1),] <- c("MS41", "299")
A115[(nrow(A115)+1),] <- c("MS6", "292")
A115[(nrow(A115)+1),] <- c("MS8", "299")
A115[(nrow(A115)+1),] <- c("PBH-3A", "297")
A115[(nrow(A115)+1),] <- c("Pcyph-TN-1", "301")
A115[(nrow(A115)+1),] <- c("PMC-9", "301")
A115[(nrow(A115)+1),] <- c("WV1", "285")
# Remove duplicates of MS29, MS30, MS33, MS34, MS36, MS42,
A115 <- A115[-c(169,170),]
A115 <- A115[-c(172,173),]
A115 <- A115[-c(178,179),]
A115 <- A115[-c(180,181),]
A115 <- A115[-c(184,185),]
A115 <- A115[-c(195,196),]
A115 <- A115[-c(271),]
A115 <- A115[-c(109),]
###########test <- A115[-c(220,221),] DUplicate of PBH5A
# Order spreadsheet
A115 <- A115[order(A115$Sample_ID),]
# Change incorrect Sample_IDs
A115$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A115$Sample_ID)
A115$Sample_ID <- gsub("Chip19_537305", "Chip19", A115$Sample_ID)
A115$Sample_ID <- gsub("Chip6_537304", "Chip6", A115$Sample_ID)
# Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# A120
A120[(nrow(A120)+1),] <- c("236-1", "224")
A120[(nrow(A120)+1),] <- c("238-3", "224")
A120[(nrow(A120)+1),] <- c("ALL1", "224")
A120[(nrow(A120)+1),] <- c("ALL10", "224")
A120[(nrow(A120)+1),] <- c("ALL13", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL20", "224")
A120[(nrow(A120)+1),] <- c("ALL9", "224")
A120[(nrow(A120)+1),] <- c("BEF-07212-01", "224")
A120[(nrow(A120)+1),] <- c("C041", "226")
A120[(nrow(A120)+1),] <- c("Chip-04", "224")
A120[(nrow(A120)+1),] <- c("Chip-15", "226")
A120[(nrow(A120)+1),] <- c("Chip-17", "226")
A120[(nrow(A120)+1),] <- c("m-07-01", "217")
A120[(nrow(A120)+1),] <- c("m-07-04", "226")
A120[(nrow(A120)+1),] <- c("MS18", "224")
A120[(nrow(A120)+1),] <- c("MS23", "226")
A120[(nrow(A120)+1),] <- c("MS24", "226")
A120[(nrow(A120)+1),] <- c("MS25", "226")
A120[(nrow(A120)+1),] <- c("MS41", "226")
A120[(nrow(A120)+1),] <- c("Pcyph-TN-2", "226")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
# Change incorrect Sample_IDs
A120$Sample_ID <- gsub("CHIP19", "Chip19", A120$Sample_ID)
A120$Sample_ID <- gsub("MS36_536674", "MS36", A120$Sample_ID)
A120$Sample_ID <- gsub("MS42_536676", "MS42", A120$Sample_ID)
A120$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A120$Sample_ID)
A120$Sample_ID <- gsub("WV1_536678", "WV1", A120$Sample_ID)
# Remove duplicates of Chip19, Chip6, MS30, MS34
A120 <- A120[-c(119,120),]
A120 <- A120[-c(126),]
A120 <- A120[-c(144,145),]
A120 <- A120[-c(198,199),]
A120 <- A120[-c(209,210),]
A120 <- A120[-c(208),]
A120 <- A120[-c(252,253),]
########Remove 16244, MS33, PMC7 duplicate!
# Order spreadsheet
A120 <- A120[order(A120$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# C1
C1[(nrow(C1)+1),] <- c("Chip-05", "318")
C1[(nrow(C1)+1),] <- c("Chip-11", "314")
C1[(nrow(C1)+1),] <- c("Chip-14", "335")
C1[(nrow(C1)+1),] <- c("m-07-06", "0")
C1[(nrow(C1)+1),] <- c("MS33", "339")
C1[(nrow(C1)+1),] <- c("PMC-2", "286")
C1[(nrow(C1)+1),] <- c("WI92", "362")
# Change incorrect Sample_IDs
C1$C1 <- gsub("OL", "0", C1$C1)
C1$Sample_ID <- gsub("Chip-19", "Chip19", C1$Sample_ID)
C1$Sample_ID <- gsub("MS17_535644", "MS17", C1$Sample_ID)
C1$Sample_ID <- gsub("MS25_535645", "MS25", C1$Sample_ID)
C1$Sample_ID <- gsub("MS41_535646", "MS41", C1$Sample_ID)
C1$Sample_ID <- gsub("MS7_535643", "MS7", C1$Sample_ID)
C1$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C1$Sample_ID)
C1$Sample_ID <- gsub("PBH2A_535648", "PBH-2A", C1$Sample_ID)
C1$Sample_ID <- gsub("PBH4A_535647", "PBH-4A", C1$Sample_ID)
# Remove duplicates of ALL11, ALL20, ALL4, MER4, MS6, WV1
C1 <- C1[-c(33,34),]
C1 <- C1[-c(53),]
C1 <- C1[-c(58),]
C1 <- C1[-c(136,137),]
C1 <- C1[-c(222,223),]
C1 <- C1[-c(299:300),]
########Remove MS2, MS32 duplicate!
# Order spreadsheet
C1 <- C1[order(C1$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# C6
C6[(nrow(C6)+1),] <- c("ALL1", "218")
C6[(nrow(C6)+1),] <- c("ALL17", "213")
C6[(nrow(C6)+1),] <- c("ALL19", "226")
C6[(nrow(C6)+1),] <- c("ALL4", "213")
C6[(nrow(C6)+1),] <- c("Chip-12", "222")
C6[(nrow(C6)+1),] <- c("Chip-13", "218")
C6[(nrow(C6)+1),] <- c("Chip-14", "213")
C6[(nrow(C6)+1),] <- c("Chip-17", "222")
C6[(nrow(C6)+1),] <- c("INHS-14795", "226")
C6[(nrow(C6)+1),] <- c("INHS-25558", "213")
C6[(nrow(C6)+1),] <- c("m-07-01", "218")
C6[(nrow(C6)+1),] <- c("m-07-06", "230")
C6[(nrow(C6)+1),] <- c("MER2", "222")
C6[(nrow(C6)+1),] <- c("Meramec-A", "218")
C6[(nrow(C6)+1),] <- c("Meramec-B", "222")
C6[(nrow(C6)+1),] <- c("MS13", "218")
C6[(nrow(C6)+1),] <- c("MS18", "213")
C6[(nrow(C6)+1),] <- c("MS2", "204")
C6[(nrow(C6)+1),] <- c("MS28", "213")
C6[(nrow(C6)+1),] <- c("MS31", "222")
C6[(nrow(C6)+1),] <- c("MS36", "218")
C6[(nrow(C6)+1),] <- c("PBH-1A", "176")
C6[(nrow(C6)+1),] <- c("PBH-2A", "176")
C6[(nrow(C6)+1),] <- c("PBH-3A", "176")
C6[(nrow(C6)+1),] <- c("PBH-5A", "209")
C6[(nrow(C6)+1),] <- c("PMC-10", "218")
C6[(nrow(C6)+1),] <- c("PMC-7", "226")
C6[(nrow(C6)+1),] <- c("PMX-4", "218")
C6[(nrow(C6)+1),] <- c("WI92", "218")
C6[(nrow(C6)+1),] <- c("WI92", "218")
C6[(nrow(C6)+1),] <- c("WI95", "218")
# Change incorrect Sample_IDs
C6$Sample_ID <- gsub("CHIP-19", "Chip19", C6$Sample_ID)
C6$Sample_ID <- gsub("MER4", "MER2", C6$Sample_ID)
C6$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP5", "TIPP6", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP6", "TIPP4", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP7", "TIPP6", C6$Sample_ID)
C6$Sample_ID <- gsub("TN7", "TN8", C6$Sample_ID)
# Remove duplicates
C6 <- C6[-c(15,16),] # 237-2
C6 <- C6[-c(47),] #
C6 <- C6[-c(125,126),] # Chip19
C6 <- C6[-c(157,158),] # m-07-07
########Remove 16244, m-07-05 duplicate!
# Order spreadsheet
C6 <- C6[order(C6$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# C105
C105[(nrow(C105)+1),] <- c("ALL14", "272")
C105[(nrow(C105)+1),] <- c("ALL15", "272")
C105[(nrow(C105)+1),] <- c("ALL7", "272")
C105[(nrow(C105)+1),] <- c("C033", "293")
C105[(nrow(C105)+1),] <- c("Chip-08", "283")
C105[(nrow(C105)+1),] <- c("Chip-09", "283")
C105[(nrow(C105)+1),] <- c("INHS-14795", "298")
C105[(nrow(C105)+1),] <- c("m-07-04", "287")
C105[(nrow(C105)+1),] <- c("m-07-07", "300")
C105[(nrow(C105)+1),] <- c("MS17", "310")
C105[(nrow(C105)+1),] <- c("MS31", "291")
C105[(nrow(C105)+1),] <- c("MS44", "310")
C105[(nrow(C105)+1),] <- c("MS5", "287")
C105[(nrow(C105)+1),] <- c("MS8", "287")
C105[(nrow(C105)+1),] <- c("PBH-4A", "295")
C105[(nrow(C105)+1),] <- c("PMC-7", "283")
C105[(nrow(C105)+1),] <- c("MS5", "287")
# Change incorrect Sample_IDs
C105$Sample_ID <- gsub("CHIP19_537805", "Chip19", C105$Sample_ID)
C105$Sample_ID <- gsub("Chip6_537804", "Chip6", C105$Sample_ID)
C105$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C105$Sample_ID)
C105$Sample_ID <- gsub("PBH-2A_537803", "PBH-2A", C105$Sample_ID)
# Remove duplicates
C105 <- C105[-c(97),] # Chip-05
C105 <- C105[-c(127),] # Chip6
########Remove A1, BEF-07212-03, MS30, MS33, MS34, MS36, MS38, MS42, PBH-5A, WV1 duplicate!
# Order spreadsheet
C105 <- C105[order(C105$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# C125
C125[(nrow(C125)+1),] <- c("238-4", "253")
C125[(nrow(C125)+1),] <- c("ALL11", "261")
C125[(nrow(C125)+1),] <- c("Chip-02", "249")
C125[(nrow(C125)+1),] <- c("Chip-15", "249")
C125[(nrow(C125)+1),] <- c("Chip-20", "249")
C125[(nrow(C125)+1),] <- c("m-07-06", "264")
C125[(nrow(C125)+1),] <- c("MER2", "257")
C125[(nrow(C125)+1),] <- c("Meramec-B", "249")
C125[(nrow(C125)+1),] <- c("MS1", "245")
C125[(nrow(C125)+1),] <- c("MS13", "253")
C125[(nrow(C125)+1),] <- c("MS16", "249")
C125[(nrow(C125)+1),] <- c("MS19", "249")
C125[(nrow(C125)+1),] <- c("MS26", "249")
C125[(nrow(C125)+1),] <- c("MS31", "249")
C125[(nrow(C125)+1),] <- c("MS33", "249")
C125[(nrow(C125)+1),] <- c("MS34", "264")
C125[(nrow(C125)+1),] <- c("MS37", "245")
C125[(nrow(C125)+1),] <- c("MS38", "249")
C125[(nrow(C125)+1),] <- c("MS44", "249")
C125[(nrow(C125)+1),] <- c("MS7", "232")
C125[(nrow(C125)+1),] <- c("PBH-3A", "227")
C125[(nrow(C125)+1),] <- c("PBH-4A", "249")
C125[(nrow(C125)+1),] <- c("PMC-6", "249")
C125[(nrow(C125)+1),] <- c("PMC-8", "249")
C125[(nrow(C125)+1),] <- c("TIPP4", "264")
# Change incorrect Sample_IDs
C125$Sample_ID <- gsub("CHIP-19", "Chip19", C125$Sample_ID)
C125$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C125$Sample_ID)
C125$Sample_ID <- gsub("TN2", "Pcyph-TN-2", C125$Sample_ID)
########Remove  duplicate!
# Order spreadsheet
C125 <- C125[order(C125$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)


# D4
D4[(nrow(D4)+1),] <- c("ALL16", "273")
D4[(nrow(D4)+1),] <- c("ALL19", "281")
D4[(nrow(D4)+1),] <- c("ALL6", "273")
D4[(nrow(D4)+1),] <- c("Chip-10", "297")
D4[(nrow(D4)+1),] <- c("Chip-15", "297")
D4[(nrow(D4)+1),] <- c("INHS-22893", "297")
D4[(nrow(D4)+1),] <- c("INHS-30476", "273")
D4[(nrow(D4)+1),] <- c("m-07-04", "285")
D4[(nrow(D4)+1),] <- c("MER2", "313")
D4[(nrow(D4)+1),] <- c("MS21", "242")
D4[(nrow(D4)+1),] <- c("MS27", "270")
D4[(nrow(D4)+1),] <- c("MS29", "242")
D4[(nrow(D4)+1),] <- c("MS3", "317")
D4[(nrow(D4)+1),] <- c("MS5", "273")
D4[(nrow(D4)+1),] <- c("PMC-10", "289")
D4[(nrow(D4)+1),] <- c("PMC-8", "289")
D4[(nrow(D4)+1),] <- c("PMC-9", "270")
D4[(nrow(D4)+1),] <- c("MS27", "270")
D4[(nrow(D4)+1),] <- c("MS27", "270")
# Change incorrect Sample_IDs
D4$Sample_ID <- gsub("CHIP19", "Chip19", D4$Sample_ID)
D4$Sample_ID <- gsub("MER4", "MER2", D4$Sample_ID)
D4$Sample_ID <- gsub("MS3_536151", "MS3", D4$Sample_ID)
D4$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D4$Sample_ID)
D4$Sample_ID <- gsub("TIPP5", "TIPP4", D4$Sample_ID)
D4$Sample_ID <- gsub("TIPP8", "TIPP6", D4$Sample_ID)
D4$Sample_ID <- gsub("TN7", "TN8", D4$Sample_ID)
# Remove duplicates
D4 <- D4[-c(43,44),] # ALL15
D4 <- D4[-c(55:59),] # ALL20
D4 <- D4[-c(65,66),] # ALL7
D4 <- D4[-c(125,126),] # Chip19
D4 <- D4[-c(127,128),] # Chip6
D4 <- D4[-c(165,166),] # MS16
D4 <- D4[-c(313:318),] # MS16
########Remove MS17, MS25, MS41, MS7,PBH4A duplicate!
# Order spreadsheet
D4 <- D4[order(D4$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)


# D10
D10[(nrow(D10)+1),] <- c("130-1", "201")
D10[(nrow(D10)+1),] <- c("130-3", "201")
D10[(nrow(D10)+1),] <- c("236-1", "201")
D10[(nrow(D10)+1),] <- c("236-2", "201")
D10[(nrow(D10)+1),] <- c("237-3", "201")
D10[(nrow(D10)+1),] <- c("238-1", "201")
D10[(nrow(D10)+1),] <- c("238-2", "201")
D10[(nrow(D10)+1),] <- c("238-4", "201")
D10[(nrow(D10)+1),] <- c("A2", "206")
D10[(nrow(D10)+1),] <- c("ALL1", "201")
D10[(nrow(D10)+1),] <- c("ALL10", "201")
D10[(nrow(D10)+1),] <- c("ALL11", "201")
D10[(nrow(D10)+1),] <- c("ALL12", "201")
D10[(nrow(D10)+1),] <- c("ALL13", "201")
D10[(nrow(D10)+1),] <- c("ALL14", "201")
D10[(nrow(D10)+1),] <- c("ALL15", "201")
D10[(nrow(D10)+1),] <- c("ALL16", "201")
D10[(nrow(D10)+1),] <- c("ALL17", "201")
D10[(nrow(D10)+1),] <- c("ALL18", "201")
D10[(nrow(D10)+1),] <- c("ALL19", "201")
D10[(nrow(D10)+1),] <- c("ALL2", "201")
D10[(nrow(D10)+1),] <- c("ALL20", "201")
D10[(nrow(D10)+1),] <- c("ALL3", "201")
D10[(nrow(D10)+1),] <- c("ALL4", "201")
D10[(nrow(D10)+1),] <- c("ALL5", "201")
D10[(nrow(D10)+1),] <- c("ALL6", "201")
D10[(nrow(D10)+1),] <- c("ALL7", "201")
D10[(nrow(D10)+1),] <- c("ALL8", "201")
D10[(nrow(D10)+1),] <- c("ALL9", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-01", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-02", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-03", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-05", "201")
D10[(nrow(D10)+1),] <- c("C024", "197")
D10[(nrow(D10)+1),] <- c("C041", "197")
D10[(nrow(D10)+1),] <- c("C219", "197")
D10[(nrow(D10)+1),] <- c("Chip-07", "201")
D10[(nrow(D10)+1),] <- c("Chip-12", "232")
D10[(nrow(D10)+1),] <- c("Chip-13", "232")
D10[(nrow(D10)+1),] <- c("Chip-16", "201")
D10[(nrow(D10)+1),] <- c("INHS-3531", "197")
D10[(nrow(D10)+1),] <- c("MS10", "232")
D10[(nrow(D10)+1),] <- c("MS16", "206")
D10[(nrow(D10)+1),] <- c("MS17", "206")
D10[(nrow(D10)+1),] <- c("MS20", "206")
D10[(nrow(D10)+1),] <- c("MS26", "206")
D10[(nrow(D10)+1),] <- c("MS27", "206")
D10[(nrow(D10)+1),] <- c("MS29", "201")
D10[(nrow(D10)+1),] <- c("MS30", "201")
D10[(nrow(D10)+1),] <- c("MS31", "201")
D10[(nrow(D10)+1),] <- c("MS33", "201")
D10[(nrow(D10)+1),] <- c("MS38", "201")
D10[(nrow(D10)+1),] <- c("MS43", "201")
D10[(nrow(D10)+1),] <- c("MS44", "194")
D10[(nrow(D10)+1),] <- c("MS5", "206")
D10[(nrow(D10)+1),] <- c("MS7", "206")
D10[(nrow(D10)+1),] <- c("Oil-City-A", "201")
D10[(nrow(D10)+1),] <- c("Oil-City-B", "201")
D10[(nrow(D10)+1),] <- c("PBH-1A", "201")
D10[(nrow(D10)+1),] <- c("PBH-2A", "201")
D10[(nrow(D10)+1),] <- c("PBH-3A", "201")
D10[(nrow(D10)+1),] <- c("PBH-4A", "232")
D10[(nrow(D10)+1),] <- c("Pcyph-TN-1", "197")
D10[(nrow(D10)+1),] <- c("PMC-1", "228")
D10[(nrow(D10)+1),] <- c("PMC-5", "241")
D10[(nrow(D10)+1),] <- c("PMC-7", "232")
D10[(nrow(D10)+1),] <- c("PMC-8", "232")
D10[(nrow(D10)+1),] <- c("PMX-2", "232")
D10[(nrow(D10)+1),] <- c("TIPP4", "201")
D10[(nrow(D10)+1),] <- c("TIPP6", "201")
D10[(nrow(D10)+1),] <- c("Pcyph-TN-2", "197")
D10[(nrow(D10)+1),] <- c("TN8", "197")
D10[(nrow(D10)+1),] <- c("UAUC3157", "197")
D10[(nrow(D10)+1),] <- c("WI95", "232")
D10[(nrow(D10)+1),] <- c("WV1", "201")
# Change incorrect Sample_IDs
D10$Sample_ID <- gsub("CHIP-19", "Chip19", D10$Sample_ID)
D10$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D10$Sample_ID)
D10$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D10$Sample_ID)

# Remove duplicates
D10 <- D10[-c(90),] # Chip-05
D10 <- D10[-c(269,270),] # PMC-3
D10 <- D10[-c(294),] # TIPP6
########Remove 14795,6271, duplicate!
# Order spreadsheet
D10 <- D10[order(D10$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# D106
D106[(nrow(D106)+1),] <- c("236-1", "272")
D106[(nrow(D106)+1),] <- c("237-1", "272")
D106[(nrow(D106)+1),] <- c("ALL14", "280")
D106[(nrow(D106)+1),] <- c("ALL15", "291")
D106[(nrow(D106)+1),] <- c("ALL18", "291")
D106[(nrow(D106)+1),] <- c("ALL3", "260")
D106[(nrow(D106)+1),] <- c("ALL6", "280")
D106[(nrow(D106)+1),] <- c("ALL8", "256")
D106[(nrow(D106)+1),] <- c("ALL9", "272")
D106[(nrow(D106)+1),] <- c("BEF-07212-02", "276")
D106[(nrow(D106)+1),] <- c("BEF-07212-05", "254")
D106[(nrow(D106)+1),] <- c("Chip-02", "260")
D106[(nrow(D106)+1),] <- c("Chip-07", "291")
D106[(nrow(D106)+1),] <- c("Chip-11", "291")
D106[(nrow(D106)+1),] <- c("Chip-15", "284")
D106[(nrow(D106)+1),] <- c("Chip-16", "272")
D106[(nrow(D106)+1),] <- c("m-07-04", "284")
D106[(nrow(D106)+1),] <- c("MS1", "276")
D106[(nrow(D106)+1),] <- c("MS12", "284")
D106[(nrow(D106)+1),] <- c("MS13", "284")
D106[(nrow(D106)+1),] <- c("MS14", "284")
D106[(nrow(D106)+1),] <- c("MS17", "294")
D106[(nrow(D106)+1),] <- c("MS18", "276")
D106[(nrow(D106)+1),] <- c("MS20", "260")
D106[(nrow(D106)+1),] <- c("MS27", "260")
D106[(nrow(D106)+1),] <- c("MS28", "256")
D106[(nrow(D106)+1),] <- c("MS31", "280")
D106[(nrow(D106)+1),] <- c("MS40", "284")
D106[(nrow(D106)+1),] <- c("PBH-2A", "242")
D106[(nrow(D106)+1),] <- c("PBH-3A", "242")
D106[(nrow(D106)+1),] <- c("PBH-4A", "276")
D106[(nrow(D106)+1),] <- c("PMC-9", "276")
D106[(nrow(D106)+1),] <- c("WI92", "280")
D106[(nrow(D106)+1),] <- c("WI94", "284")
# Change incorrect Sample_IDs
D106$Sample_ID <- gsub("CHIP-19", "Chip19", D106$Sample_ID)
D106$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D106$Sample_ID)
D106$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D106$Sample_ID)
# Remove duplicates
D106 <- D106[-c(150),] # MS13
D106 <- D106[-c(9),] # 236-1
########Remove duplicate!
# Order spreadsheet
D106 <- D106[order(D106$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# D113
D113[(nrow(D113)+1),] <- c("236-1", "274")
D113[(nrow(D113)+1),] <- c("236-2", "289")
D113[(nrow(D113)+1),] <- c("237-1", "572")
D113[(nrow(D113)+1),] <- c("237-2", "289")
D113[(nrow(D113)+1),] <- c("238-3", "281")
D113[(nrow(D113)+1),] <- c("238-4", "289")
D113[(nrow(D113)+1),] <- c("A2", "296")
D113[(nrow(D113)+1),] <- c("ALL11", "281")
D113[(nrow(D113)+1),] <- c("ALL12", "277")
D113[(nrow(D113)+1),] <- c("ALL14", "277")
D113[(nrow(D113)+1),] <- c("ALL17", "269")
D113[(nrow(D113)+1),] <- c("ALL18", "289")
D113[(nrow(D113)+1),] <- c("ALL6", "296")
D113[(nrow(D113)+1),] <- c("ALL7", "296")
D113[(nrow(D113)+1),] <- c("BEF-07212-01", "484")
D113[(nrow(D113)+1),] <- c("C024", "300")
D113[(nrow(D113)+1),] <- c("C033", "285")
D113[(nrow(D113)+1),] <- c("Chip-05", "296")
D113[(nrow(D113)+1),] <- c("Chip-11", "296")
D113[(nrow(D113)+1),] <- c("Chip-12", "296")
D113[(nrow(D113)+1),] <- c("Chip-13", "296")
D113[(nrow(D113)+1),] <- c("Chip-20", "296")
D113[(nrow(D113)+1),] <- c("INHS-16244", "296")
D113[(nrow(D113)+1),] <- c("INHS-25558", "296")
D113[(nrow(D113)+1),] <- c("INHS-3531", "277")
D113[(nrow(D113)+1),] <- c("INHS-6271", "277")
D113[(nrow(D113)+1),] <- c("m-07-05", "376")
D113[(nrow(D113)+1),] <- c("Meramec-A", "399")
D113[(nrow(D113)+1),] <- c("Meramec-B", "407")
D113[(nrow(D113)+1),] <- c("MS1", "300")
D113[(nrow(D113)+1),] <- c("MS10", "296")
D113[(nrow(D113)+1),] <- c("MS13", "296")
D113[(nrow(D113)+1),] <- c("MS14", "300")
D113[(nrow(D113)+1),] <- c("MS16", "296")
D113[(nrow(D113)+1),] <- c("MS18", "296")
D113[(nrow(D113)+1),] <- c("MS23", "296")
D113[(nrow(D113)+1),] <- c("MS26", "300")
D113[(nrow(D113)+1),] <- c("MS27", "296")
D113[(nrow(D113)+1),] <- c("MS3", "296")
D113[(nrow(D113)+1),] <- c("MS31", "296")
D113[(nrow(D113)+1),] <- c("MS32", "296")
D113[(nrow(D113)+1),] <- c("MS4", "296")
D113[(nrow(D113)+1),] <- c("MS42", "296")
D113[(nrow(D113)+1),] <- c("MS43", "296")
D113[(nrow(D113)+1),] <- c("MS5", "296")
D113[(nrow(D113)+1),] <- c("MS6", "296")
D113[(nrow(D113)+1),] <- c("MS8", "296")
D113[(nrow(D113)+1),] <- c("MS9", "296")
D113[(nrow(D113)+1),] <- c("Oil-City-A", "325")
D113[(nrow(D113)+1),] <- c("Oil-City-B", "293")
D113[(nrow(D113)+1),] <- c("PBH-3A", "321")
D113[(nrow(D113)+1),] <- c("PMC-10", "380")
D113[(nrow(D113)+1),] <- c("PMC-2", "321")
D113[(nrow(D113)+1),] <- c("PMC-3", "346")
D113[(nrow(D113)+1),] <- c("PMC-6", "325")
D113[(nrow(D113)+1),] <- c("PMC-7", "403")
D113[(nrow(D113)+1),] <- c("PMC-8", "321")
D113[(nrow(D113)+1),] <- c("PMC-9", "317")
D113[(nrow(D113)+1),] <- c("PMX-1", "317")
D113[(nrow(D113)+1),] <- c("WI92", "300")
D113[(nrow(D113)+1),] <- c("WV1", "277")
# Change incorrect Sample_IDs
D113$Sample_ID <- gsub("CHIP-19", "Chip19", D113$Sample_ID)
D113$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D113$Sample_ID)
D113$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D113$Sample_ID)
# Remove duplicates
D113 <- D113[-c(209,210),] # MS33
D113 <- D113[-c(211,212),] # MS34
D113 <- D113[-c(287,288),] # TIPP4
D113 <- D113[-c(291,292),] # Pcyph-TN-2
D113 <- D113[-c(293,294),] # TN8
########Remove 9470 duplicate!
# Order spreadsheet
D113 <- D113[order(D113$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# D114
D114[(nrow(D114)+1),] <- c("ALL12", "244")
D114[(nrow(D114)+1),] <- c("ALL16", "244")
D114[(nrow(D114)+1),] <- c("ALL8", "244")
D114[(nrow(D114)+1),] <- c("BEF-07212-01", "244")
D114[(nrow(D114)+1),] <- c("Chip-07", "244")
D114[(nrow(D114)+1),] <- c("Chip-09", "244")
D114[(nrow(D114)+1),] <- c("Chip-11", "244")
D114[(nrow(D114)+1),] <- c("Chip-13", "244")
D114[(nrow(D114)+1),] <- c("Chip-15", "244")
D114[(nrow(D114)+1),] <- c("Chip-17", "244")
D114[(nrow(D114)+1),] <- c("Chip-18", "240")
D114[(nrow(D114)+1),] <- c("Chip6", "244")
D114[(nrow(D114)+1),] <- c("INHS-16244", "244")
D114[(nrow(D114)+1),] <- c("INHS-3531", "244")
D114[(nrow(D114)+1),] <- c("m-07-06", "249")
D114[(nrow(D114)+1),] <- c("Meramec-B", "240")
D114[(nrow(D114)+1),] <- c("MS10", "240")
D114[(nrow(D114)+1),] <- c("MS13", "244")
D114[(nrow(D114)+1),] <- c("MS19", "244")
D114[(nrow(D114)+1),] <- c("MS27", "244")
D114[(nrow(D114)+1),] <- c("MS30", "240")
D114[(nrow(D114)+1),] <- c("MS5", "244")
D114[(nrow(D114)+1),] <- c("Oil-City-A", "261")
D114[(nrow(D114)+1),] <- c("Oil-City-B", "244")
D114[(nrow(D114)+1),] <- c("PBH-1A", "254")
D114[(nrow(D114)+1),] <- c("PBH-3A", "254")
D114[(nrow(D114)+1),] <- c("Pcyph-TN-1", "244")
D114[(nrow(D114)+1),] <- c("PMC-2", "240")
D114[(nrow(D114)+1),] <- c("PMC-3", "236")
D114[(nrow(D114)+1),] <- c("PMX-3", "249")
D114[(nrow(D114)+1),] <- c("Pcyph-TN-2", "236")
D114[(nrow(D114)+1),] <- c("WI92", "249")
# Change incorrect Sample_IDs
D114$Sample_ID <- gsub("CHIP-19", "Chip19", D114$Sample_ID)
D114$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D114$Sample_ID)
D114$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D114$Sample_ID)
# Remove duplicates
D114 <- D114[-c(94),] # Chip-05
D114 <- D114[-c(149),] # m-07-07
########Remove 6271 duplicate!
# Order spreadsheet
D114 <- D114[order(D114$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# D119
D119[(nrow(D119)+1),] <- c("130-3", "298")
D119[(nrow(D119)+1),] <- c("238-1", "306")
D119[(nrow(D119)+1),] <- c("ALL10", "302")
D119[(nrow(D119)+1),] <- c("ALL12", "327")
D119[(nrow(D119)+1),] <- c("ALL12", "244")
D119[(nrow(D119)+1),] <- c("ALL2", "298")
D119[(nrow(D119)+1),] <- c("ALL3", "294")
D119[(nrow(D119)+1),] <- c("BEF-07212-05", "302")
D119[(nrow(D119)+1),] <- c("Chip-08", "306")
D119[(nrow(D119)+1),] <- c("Chip-12", "298")
D119[(nrow(D119)+1),] <- c("Chip-20", "306")
D119[(nrow(D119)+1),] <- c("MS18", "302")
D119[(nrow(D119)+1),] <- c("MS20", "306")
D119[(nrow(D119)+1),] <- c("MS23", "310")
D119[(nrow(D119)+1),] <- c("MS25", "310")
D119[(nrow(D119)+1),] <- c("MS29", "310")
D119[(nrow(D119)+1),] <- c("MS33", "302")
D119[(nrow(D119)+1),] <- c("MS42", "302")
D119[(nrow(D119)+1),] <- c("PBH-1A", "332")
D119[(nrow(D119)+1),] <- c("PMC-2", "306")
D119[(nrow(D119)+1),] <- c("PMC-8", "298")
D119[(nrow(D119)+1),] <- c("PMX-5", "302")
D119[(nrow(D119)+1),] <- c("WV1", "306")
# Change incorrect Sample_IDs
D119$Sample_ID <- gsub("CHIP-19", "Chip19", D119$Sample_ID)
D119$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D119$Sample_ID)
D119$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D119$Sample_ID)
# Order spreadsheet
D119 <- D119[order(D119$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)

# D125
D125[(nrow(D125)+1),] <- c("130-1", "278")
D125[(nrow(D125)+1),] <- c("236-2", "260")
D125[(nrow(D125)+1),] <- c("Chip-03", "249")
D125[(nrow(D125)+1),] <- c("Chip-10", "245")
D125[(nrow(D125)+1),] <- c("Chip-11", "264")
D125[(nrow(D125)+1),] <- c("Chip-14", "278")
D125[(nrow(D125)+1),] <- c("Chip-16", "241")
D125[(nrow(D125)+1),] <- c("INHS-6271", "252")
D125[(nrow(D125)+1),] <- c("m-07-03", "271")
D125[(nrow(D125)+1),] <- c("m-07-06", "256")
D125[(nrow(D125)+1),] <- c("MS14", "256")
D125[(nrow(D125)+1),] <- c("MS22", "260")
D125[(nrow(D125)+1),] <- c("MS29", "256")
D125[(nrow(D125)+1),] <- c("MS3", "252")
D125[(nrow(D125)+1),] <- c("MS9", "274")
D125[(nrow(D125)+1),] <- c("Oil-City-A", "267")
D125[(nrow(D125)+1),] <- c("PMC-8", "267")
D125[(nrow(D125)+1),] <- c("WI93", "249")
# Change incorrect Sample_IDs
D125$Sample_ID <- gsub("CHIP-19", "Chip19", D125$Sample_ID)
D125$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D125$Sample_ID)
D125$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D125$Sample_ID)
# Remove duplicates
D125 <- D125[-c(145:147),] # m-07-07
D125 <- D125[-c(147),] # m-07-07
########Remove Chip-05, PMX-2 duplicate!
# Order spreadsheet
D125 <- D125[order(D125$Sample_ID),]
#Spread data
#A115$high_low <- rep.int(dummy, nrow(A115)/2)
#A115$new_genos <- paste(A115$loci, "_", A115$high_low)
#test <- gather(A115, key = "loci", value = "genotypes",
                      #colnames(A115[,-1]))
#test2 <- test[,-c(2,4)]
#test_wide <- spread(test2, new_genos, genotypes, fill = 0)
```





















