# This code was used manipulate data from the raw data output from Genemarker to the input data file for GenAlex.

## Set working directory
setwd("C:/Users/Sara/Documents/EEB_2016-2018/Peak tables/Intermediate_files")


## Packages
```{r}
if (!require("readr")) install.packages("readr")
library(readr)

if (!require("reshape2")) install.packages("reshape2")
library(reshape2)

if (!require("dplyr")) install.packages("dplyr")
library(dplyr)

if (!require("gsubfn")) install.packages("gsubfn")
library(gsubfn)

if (!require("stringr")) install.packages("stringr")
library(stringr)

if (!require("tidyr")) install.packages("tidyr")
library(tidyr)
```

# Converting raw data from Genemarker into complete dataset by locus

## A103
```{r}
A103_raw <- read.table("A103_raw.csv", sep = ",", na.strings = c("", "NA"))
A103 <- A103_raw[,-c(2:6)] #cut out unnecessary columns
A103 <- A103[,-c(3:8)] #cut out unnecessary columns
names(A103) <- c("Sample_ID", "A103") #rename columns
A103[A103 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A103 = A103 %>% na.omit() #omit all NAs
A103$Sample_ID <- str_sub(A103$Sample, 5, 17) #Remove lane name and underscore
A103$Sample_ID <- strapplyc(A103$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A103 <- A103[order(A103$Sample_ID),]

View(A103)
```

## A115
```{r}
A115_raw <- read.table("A115_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A115 <- A115_raw[,-c(2:6)] #cut out unnecessary columns
A115 <- A115[,-c(3:8)] #cut out unnecessary columns
names(A115) <- c("Sample_ID", "A115") #rename columns
A115[A115 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A115 = A115 %>% na.omit() #omit NAs again
A115$Sample_ID <- str_sub(A115$Sample, 5, 18) #Remove lane name and underscore
A115$Sample_ID <- strapplyc(A115$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
A115 <- A115[order(A115$Sample_ID),]
View(A115)
```


## A120
```{r}
A120_raw <- read.table("A120_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A120 <- A120_raw[,-c(2:6)] #cut out unnecessary columns
A120 <- A120[,-c(3:8)] #cut out unnecessary columns
names(A120) <- c("Sample_ID", "A120") #rename columns
A120[A120 == "Sample"] <- NA #convert sample to NAs so they can be omitted
A120 = A120 %>% na.omit() #omit NAs again
A120$Sample_ID <- str_sub(A120$Sample, 5, 18) #Remove lane name and underscore
A120$Sample_ID <- strapplyc(A120$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A120 <- A120[order(A120$Sample_ID),]

View(A120)
```


## C1
```{r}
C1_raw <- read.table("C1_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C1 <- C1_raw[,-c(2:6)] #cut out unnecessary columns
C1 <- C1[,-c(3:8)] #cut out unnecessary columns
names(C1) <- c("Sample_ID", "C1") #rename columns
C1[C1 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C1 = C1 %>% na.omit() #omit NAs again
C1$Sample_ID <- str_sub(C1$Sample, 5, 18) #Remove lane name and underscore
C1$Sample_ID <- strapplyc(C1$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C1 <- C1[order(C1$Sample_ID),]

View(C1)
```


## C6
```{r}
C6_raw <- read.table("C6_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C6 <- C6_raw[,-c(2:6)] #cut out unnecessary columns
C6 <- C6[,-c(3:8)] #cut out unnecessary columns
names(C6) <- c("Sample_ID", "C6") #rename columns
C6[C6 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C6 = C6 %>% na.omit() #omit NAs again
C6$Sample_ID <- str_sub(C6$Sample, 5, 18) #Remove lane name and underscore
C6$Sample_ID <- strapplyc(C6$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C6 <- C6[order(C6$Sample_ID),]

View(C6)
```


## C105
```{r}
C105_raw <- read.table("C105_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C105 <- C105_raw[,-c(2:6)] #cut out unnecessary columns
C105 <- C105[,-c(3:8)] #cut out unnecessary columns
names(C105) <- c("Sample_ID", "C105") #rename columns
C105[C105 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C105 = C105 %>% na.omit() #omit NAs again
C105$Sample_ID <- str_sub(C105$Sample, 5, 18) #Remove lane name and underscore
C105$Sample_ID <- strapplyc(C105$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C105 <- C105[order(C105$Sample_ID),]

View(C105)
```


## C125
```{r}
C125_raw <- read.table("C125_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C125 <- C125_raw[,-c(2:6)] #cut out unnecessary columns
C125 <- C125[,-c(3:8)] #cut out unnecessary columns
names(C125) <- c("Sample_ID", "C125") #rename columns
C125[C125 == "Sample"] <- NA #convert sample to NAs so they can be omitted
C125 = C125 %>% na.omit() #omit NAs again
C125$Sample_ID <- str_sub(C125$Sample, 5, 18) #Remove lane name and underscore
C125$Sample_ID <- strapplyc(C125$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C125 <- C125[order(C125$Sample_ID),]

View(C125)
```


## D4
```{r}
D4_raw <- read.table("D4_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D4 <- D4_raw[,-c(2:6)] #cut out unnecessary columns
D4 <- D4[,-c(3:8)] #cut out unnecessary columns
names(D4) <- c("Sample_ID", "D4") #rename columns
D4[D4 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D4 = D4 %>% na.omit() #omit NAs again
D4$Sample_ID <- str_sub(D4$Sample, 5, 18) #Remove lane name and underscore
D4$Sample_ID <- strapplyc(D4$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D4 <- D4[order(D4$Sample_ID),]

View(D4)
```


## D10
```{r}
D10_raw <- read.table("D10_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D10 <- D10_raw[,-c(2:6)] #cut out unnecessary columns
D10 <- D10[,-c(3:8)] #cut out unnecessary columns
names(D10) <- c("Sample_ID", "D10") #rename columns
D10[D10 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D10 = D10 %>% na.omit() #omit NAs again
D10$Sample_ID <- str_sub(D10$Sample, 5, 18) #Remove lane name and underscore
D10$Sample_ID <- strapplyc(D10$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D10 <- D10[order(D10$Sample_ID),]

View(D10)
```


## D106
```{r}
D106_raw <- read.table("D106_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D106 <- D106_raw[,-c(2:6)] #cut out unnecessary columns
D106 <- D106[,-c(3:8)] #cut out unnecessary columns
names(D106) <- c("Sample_ID", "D106") #rename columns
D106[D106 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D106 = D106 %>% na.omit() #omit NAs again
D106$Sample_ID <- str_sub(D106$Sample, 5, 18) #Remove lane name and underscore
D106$Sample_ID <- strapplyc(D106$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D106 <- D106[order(D106$Sample_ID),]

View(D106)
```


## D113
```{r}
D113_raw <- read.table("D113_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D113 <- D113_raw[,-c(2:6)] #cut out unnecessary columns
D113 <- D113[,-c(3:8)] #cut out unnecessary columns
names(D113) <- c("Sample_ID", "D113") #rename columns
D113[D113 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D113 = D113 %>% na.omit() #omit NAs again
D113$Sample_ID <- str_sub(D113$Sample, 5, 18) #Remove lane name and underscore
D113$Sample_ID <- strapplyc(D113$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D113 <- D113[order(D113$Sample_ID),]

View(D113)
```

## D114
```{r}
D114_raw <- read.table("D114_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D114 <- D114_raw[,-c(2:6)] #cut out unnecessary columns
D114 <- D114[,-c(3:8)] #cut out unnecessary columns
names(D114) <- c("Sample_ID", "D114") #rename columns
D114[D114 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D114 = D114 %>% na.omit() #omit NAs again
D114$Sample_ID <- str_sub(D114$Sample, 5, 18) #Remove lane name and underscore
D114$Sample_ID <- strapplyc(D114$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D114 <- D114[order(D114$Sample_ID),]

View(D114)
```

## D119
```{r}
D119_raw <- read.table("D119_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D119 <- D119_raw[,-c(2:6)] #cut out unnecessary columns
D119 <- D119[,-c(3:8)] #cut out unnecessary columns
names(D119) <- c("Sample_ID", "D119") #rename columns
D119[D119 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D119 = D119 %>% na.omit() #omit NAs again
D119$Sample_ID <- str_sub(D119$Sample, 5, 18) #Remove lane name and underscore
D119$Sample_ID <- strapplyc(D119$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D119 <- D119[order(D119$Sample_ID),]

View(D119)
```


## D125
```{r}
D125_raw <- read.table("D125_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D125 <- D125_raw[,-c(2:6)] #cut out unnecessary columns
D125 <- D125[,-c(3:8)] #cut out unnecessary columns
names(D125) <- c("Sample_ID", "D125") #rename columns
D125[D125 == "Sample"] <- NA #convert sample to NAs so they can be omitted
D125 = D125 %>% na.omit() #omit NAs again
D125$Sample_ID <- str_sub(D125$Sample, 5, 18) #Remove lane name and underscore
D125$Sample_ID <- strapplyc(D125$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D125 <- D125[order(D125$Sample_ID),]

View(D125)
```

# Converting data from Genemarker for 12 Wisconsin samples

## A103 
```{r}
A103_wisraw <- read.table("A103_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A103_wis <- A103_wisraw[,-c(2:6)] #cut out unnecessary columns
A103_wis <- A103_wis[,-c(3:8)] #cut out unnecessary columns
names(A103_wis) <- c("Sample_ID", "A103") #rename columns
A103_wis[A103_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
A103_wis[A103_wis == "OL"] <- NA #convert sample to NAs so they can be omitted
A103_wis = A103_wis %>% na.omit() #omit NAs again
A103_wis$Sample_ID <- str_sub(A103_wis$Sample, 5, 17) #Remove lane name and underscore
A103_wis$Sample_ID <- strapplyc(A103_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
A103_wis <- A103_wis[order(A103_wis$Sample_ID),]

View(A103_wis)
```

## A115
```{r}
A115_wisraw <- read.table("A115_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A115_wis <- A115_wisraw[,-c(2:6)] #cut out unnecessary columns
A115_wis <- A115_wis[,-c(3:8)] #cut out unnecessary columns
names(A115_wis) <- c("Sample_ID", "A115") #rename columns
A115_wis[A115_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
A115_wis[A115_wis == "OL"] <- NA #convert sample to NAs so they can be omitted
A115_wis = A115_wis %>% na.omit() #omit NAs again
A115_wis$Sample_ID <- str_sub(A115_wis$Sample, 5, 17) #Remove lane name and underscore
A115_wis$Sample_ID <- strapplyc(A115_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
A115_wis <- A115_wis[order(A115_wis$Sample_ID),]

View(A115_wis)
```

## A120
```{r}
A120_wisraw <- read.table("A120_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
A120_wis <- A120_wisraw[,-c(2:6)] #cut out unnecessary columns
A120_wis <- A120_wis[,-c(3:8)] #cut out unnecessary columns
names(A120_wis) <- c("Sample_ID", "A120") #rename columns
A120_wis[A120_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
A120_wis = A120_wis %>% na.omit() #omit NAs again
A120_wis$Sample_ID <- str_sub(A120_wis$Sample, 5, 18) #Remove lane name and underscore
A120_wis$Sample_ID <- strapplyc(A120_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
A120_wis <- A120_wis[order(A120_wis$Sample_ID),]

View(A120_wis)
```


## C1
```{r}
C1_wisraw <- read.table("C1_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C1_wis <- C1_wisraw[,-c(2:5)] #cut out unnecessary columns
C1_wis <- C1_wis[,-c(4:8)] #cut out unnecessary columns
names(C1_wis) <- c("Sample_ID", "C1") #rename columns
C1_wis[C1_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C1_wis = C1_wis %>% na.omit() #omit all NAs
C1_wis$Sample_ID <- str_sub(C1_wis$Sample, 5, 18) #Remove lane name and underscore
C1_wis$Sample_ID <- strapplyc(C1_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C1_wis <- C1_wis[order(C1_wis$Sample_ID),]

View(C1_wis)
```


## C6
```{r}
C6_wisraw <- read.table("C6_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C6_wis <- C6_wisraw[,-c(2:6)] #cut out unnecessary columns
C6_wis <- C6_wis[,-c(3:8)] #cut out unnecessary columns
names(C6_wis) <- c("Sample_ID", "C6") #rename columns
C6_wis[C6_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C6_wis = C6_wis %>% na.omit() #omit NAs again
C6_wis$Sample_ID <- str_sub(C6_wis$Sample, 5, 18) #Remove lane name and underscore
C6_wis$Sample_ID <- strapplyc(C6_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C6_wis <- C6_wis[order(C6_wis$Sample_ID),]

View(C6_wis)
```


## C105
```{r}
C105_wisraw <- read.table("C105_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C105_wis <- C105_wisraw[,-c(2:6)] #cut out unnecessary columns
C105_wis <- C105_wis[,-c(3:8)] #cut out unnecessary columns
names(C105_wis) <- c("Sample_ID", "C105") #rename columns
C105_wis[C105_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C105_wis = C105_wis %>% na.omit() #omit NAs again
C105_wis$Sample_ID <- str_sub(C105_wis$Sample, 5, 18) #Remove lane name and underscore
C105_wis$Sample_ID <- strapplyc(C105_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C105_wis <- C105_wis[order(C105_wis$Sample_ID),]

View(C105_wis)
```


## C125
```{r}
C125_wisraw <- read.table("C125_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
C125_wis <- C125_wisraw[,-c(2:6)] #cut out unnecessary columns
C125_wis <- C125_wis[,-c(3:8)] #cut out unnecessary columns
names(C125_wis) <- c("Sample_ID", "C125") #rename columns
C125_wis[C125_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
C125_wis = C125_wis %>% na.omit() #omit NAs again
C125_wis$Sample_ID <- str_sub(C125_wis$Sample, 5, 18) #Remove lane name and underscore
C125_wis$Sample_ID <- strapplyc(C125_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
C125_wis <- C125_wis[order(C125_wis$Sample_ID),]

View(C125_wis)
```


## D4
```{r}
D4_wisraw <- read.table("D4_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D4_wis <- D4_wisraw[,-c(2:6)] #cut out unnecessary columns
D4_wis <- D4_wis[,-c(3:8)] #cut out unnecessary columns
names(D4_wis) <- c("Sample_ID", "D4") #rename columns
D4_wis[D4_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D4_wis = D4_wis %>% na.omit() #omit all NAs
D4_wis$Sample_ID <- str_sub(D4_wis$Sample, 5, 18) #Remove lane name and underscore
D4_wis$Sample_ID <- strapplyc(D4_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D4_wis <- D4_wis[order(D4_wis$Sample_ID),]

View(D4_wis)
```


## D10
```{r}
D10_wisraw <- read.table("D10_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D10_wis <- D10_wisraw[,-c(2:6)] #cut out unnecessary columns
D10_wis <- D10_wis[,-c(3:8)] #cut out unnecessary columns
names(D10_wis) <- c("Sample_ID", "D10") #rename columns
D10_wis[D10_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D10_wis = D10_wis %>% na.omit() #omit NAs again
D10_wis$Sample_ID <- str_sub(D10_wis$Sample, 5, 18) #Remove lane name and underscore
D10_wis$Sample_ID <- strapplyc(D10_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D10_wis <- D10_wis[order(D10_wis$Sample_ID),]

View(D10_wis)
```


## D113
```{r}
D113_wisraw <- read.table("D113_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D113_wis <- D113_wisraw[,-c(2:6)] #cut out unnecessary columns
D113_wis <- D113_wis[,-c(3:8)] #cut out unnecessary columns
names(D113_wis) <- c("Sample_ID", "D113") #rename columns
D113_wis[D113_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D113_wis = D113_wis %>% na.omit() #omit NAs again
D113_wis$Sample_ID <- str_sub(D113_wis$Sample, 5, 18) #Remove lane name and underscore
D113_wis$Sample_ID <- strapplyc(D113_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D113_wis <- D113_wis[order(D113_wis$Sample_ID),]

View(D113_wis)
```


## D114
```{r}
D114_wisraw <- read.table("D114_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D114_wis <- D114_wisraw[,-c(2:6)] #cut out unnecessary columns
D114_wis <- D114_wis[,-c(3:8)] #cut out unnecessary columns
names(D114_wis) <- c("Sample_ID", "D114") #rename columns
D114_wis[D114_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D114_wis = D114_wis %>% na.omit() #omit NAs again
D114_wis$Sample_ID <- str_sub(D114_wis$Sample, 5, 18) #Remove lane name and underscore
D114_wis$Sample_ID <- strapplyc(D114_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D114_wis <- D114_wis[order(D114_wis$Sample_ID),]

View(D114_wis)
```


## D119
```{r}
D119_wisraw <- read.table("D119_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D119_wis <- D119_wisraw[,-c(2:6)] #cut out unnecessary columns
D119_wis <- D119_wis[,-c(3:8)] #cut out unnecessary columns
names(D119_wis) <- c("Sample_ID", "D119") #rename columns
D119_wis[D119_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D119_wis = D119_wis %>% na.omit() #omit NAs again
D119_wis$Sample_ID <- str_sub(D119_wis$Sample, 5, 18) #Remove lane name and underscore
D119_wis$Sample_ID <- strapplyc(D119_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D119_wis <- D119_wis[order(D119_wis$Sample_ID),]

View(D119_wis)
```



## D106
```{r}
D106_wisraw <- read.table("D106_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D106_wis <- D106_wisraw[,-c(2:6)] #cut out unnecessary columns
D106_wis <- D106_wis[,-c(3:8)] #cut out unnecessary columns
names(D106_wis) <- c("Sample_ID", "D106") #rename columns
D106_wis[D106_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D106_wis = D106_wis %>% na.omit() #omit NAs again
D106_wis$Sample_ID <- str_sub(D106_wis$Sample, 5, 18) #Remove lane name and underscore
D106_wis$Sample_ID <- strapplyc(D106_wis$Sample_ID, "(.*)_", simplify = T) #Reomve lab ID after underscore
D106_wis <- D106_wis[order(D106_wis$Sample_ID),]

View(D106_wis)
```


## D125
```{r}
D125_wisraw <- read.table("D125_wis_raw.csv", sep = ",", na.strings = c("", "NA")) #read in data
D125_wis <- D125_wisraw[,-c(2:6)] #cut out unnecessary columns
D125_wis <- D125_wis[,-c(3:8)] #cut out unnecessary columns
names(D125_wis) <- c("Sample_ID", "D125") #rename columns
D125_wis[D125_wis == "Sample"] <- NA #convert sample to NAs so they can be omitted
D125_wis = D125_wis %>% na.omit() #omit NAs again
D125_wis$Sample_ID <- str_sub(D125_wis$Sample, 5, 18) #Remove lane name and underscore
D125_wis$Sample_ID <- strapplyc(D125_wis$Sample_ID, "(.*)_", simplify = T) #Remove lab ID after underscore
D125_wis <- D125_wis[order(D125_wis$Sample_ID),]

View(D125_wis)
```




# Add duplicate row for second homozygous allele and spread data
```{r}
# Must be done at each locus
# A103 locus
A103[(nrow(A103)+1),] <- c("ALL3", "244")
A103[(nrow(A103)+1),] <- c("ALL10", "242")
A103[(nrow(A103)+1),] <- c("ALL11", "242")
A103[(nrow(A103)+1),] <- c("ALL4", "242")
A103[(nrow(A103)+1),] <- c("ALL7", "244")
A103[(nrow(A103)+1),] <- c("BEF-07212-01", "244")
A103[(nrow(A103)+1),] <- c("C041", "251")
A103[(nrow(A103)+1),] <- c("INHS-25558", "246")
A103[(nrow(A103)+1),] <- c("m-07-07", "257")
A103[(nrow(A103)+1),] <- c("MS33", "244")
A103[(nrow(A103)+1),] <- c("MS36", "249")
A103[(nrow(A103)+1),] <- c("Pcyph-TN-2", "240")
A103[(nrow(A103)+1),] <- c("PMC-8", "249")
A103 <- A103[order(A103$Sample_ID),]
# Remove Chip 5 OL call
A103 <- A103[-c(94),]
# Remove INHS-16244 duplicate
A103 <- A103[-c(129),]
# Replace incorrect Sample_IDs
A103$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A103$Sample_ID)
# Spread data
dummy <- c("high", "low") # Create dummy vector
A103_new <- A103 # Create new dataframe 
A103_new$high_low <- rep.int(dummy, nrow(A103_new)/2) # Add extra column delineating high and low alleles
A103_new <- gather(A103_new, key = "loci", value = "genotypes",
                      colnames(A103_new[,-1])) # Gather data
A103_new$high_low <- rep.int(dummy, nrow(A103_new)/2) # Reallocate high and low designations
A103_new <- A103_new[,-c(2)] # Remove loci column
A103_new <- A103_new[-c(311:620),] # Remove doubles? Not sure where they came from
A103_new_wide <- spread(A103_new, high_low, genotypes, fill = 0) # Spread data
names(A103_new_wide) <- c("Sample_ID", "A103_high", "A103_low") # Rename columns

# A115 locus
A115[(nrow(A115)+1),] <- c("130-3", "310")
A115[(nrow(A115)+1),] <- c("237-1", "301")
A115[(nrow(A115)+1),] <- c("C024", "301")
A115[(nrow(A115)+1),] <- c("Chip-04", "292")
A115[(nrow(A115)+1),] <- c("Chip-10", "303")
A115[(nrow(A115)+1),] <- c("Chip-14", "310")
A115[(nrow(A115)+1),] <- c("Chip6_537304", "285")
A115[(nrow(A115)+1),] <- c("m-07-05", "292")
A115[(nrow(A115)+1),] <- c("Meramec-A", "292")
A115[(nrow(A115)+1),] <- c("Meramec-B", "285")
A115[(nrow(A115)+1),] <- c("MS17", "299")
A115[(nrow(A115)+1),] <- c("MS2", "301")
A115[(nrow(A115)+1),] <- c("MS20", "301")
A115[(nrow(A115)+1),] <- c("MS22", "285")
A115[(nrow(A115)+1),] <- c("MS23", "285")
A115[(nrow(A115)+1),] <- c("MS25", "292")
A115[(nrow(A115)+1),] <- c("MS27", "292")
A115[(nrow(A115)+1),] <- c("MS28", "299")
A115[(nrow(A115)+1),] <- c("MS3", "285")
A115[(nrow(A115)+1),] <- c("MS37", "301")
A115[(nrow(A115)+1),] <- c("MS23", "285")
A115[(nrow(A115)+1),] <- c("MS39", "292")
A115[(nrow(A115)+1),] <- c("MS41", "299")
A115[(nrow(A115)+1),] <- c("MS6", "292")
A115[(nrow(A115)+1),] <- c("MS8", "299")
A115[(nrow(A115)+1),] <- c("PBH-3A", "297")
A115[(nrow(A115)+1),] <- c("Pcyph-TN-1", "301")
A115[(nrow(A115)+1),] <- c("PMC-9", "301")
A115[(nrow(A115)+1),] <- c("WV1", "285")
# Remove duplicates of MS29, MS30, MS33, MS34, MS36, MS42, PBH5A
A115 <- A115[-c(169,170),]
A115 <- A115[-c(172,173),]
A115 <- A115[-c(178,179),]
A115 <- A115[-c(180,181),]
A115 <- A115[-c(184,185),]
A115 <- A115[-c(195,196),]
A115 <- A115[-c(271),]
A115 <- A115[-c(109),]
A115 <- A115[-c(245,246),] # Remove 338 allele
# Order spreadsheet
A115 <- A115[order(A115$Sample_ID),]
# Change incorrect Sample_IDs
A115$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A115$Sample_ID)
A115$Sample_ID <- gsub("Chip19_537305", "Chip19", A115$Sample_ID)
A115$Sample_ID <- gsub("Chip6_537304", "Chip6", A115$Sample_ID)
# Spread data
dummy <- c("high", "low") # Create dummy vector
A115_new <- A115 # Create new dataframe 
A115_new$high_low <- rep.int(dummy, nrow(A115_new)/2) # Add extra column delineating high and low alleles
A115_new <- gather(A115_new, key = "loci", value = "genotypes",
                      colnames(A115_new[,-1])) # Gather data
A115_new$high_low <- rep.int(dummy, nrow(A115_new)/2) # Reallocate high and low designations
A115_new <- A115_new[,-c(2)] # Remove loci column
A115_new <- A115_new[-c(297:620),] # Remove doubles? Not sure where they came from
A115_new_wide <- spread(A115_new, high_low, genotypes, fill = 0) # Spread data
names(A115_new_wide) <- c("Sample_ID", "A115_high", "A115_low") # Rename columns

# A120
A120[(nrow(A120)+1),] <- c("236-1", "224")
A120[(nrow(A120)+1),] <- c("238-3", "224")
A120[(nrow(A120)+1),] <- c("ALL1", "224")
A120[(nrow(A120)+1),] <- c("ALL10", "224")
A120[(nrow(A120)+1),] <- c("ALL13", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL20", "224")
A120[(nrow(A120)+1),] <- c("ALL9", "224")
A120[(nrow(A120)+1),] <- c("BEF-07212-01", "224")
A120[(nrow(A120)+1),] <- c("C041", "226")
A120[(nrow(A120)+1),] <- c("Chip-04", "224")
A120[(nrow(A120)+1),] <- c("Chip-15", "226")
A120[(nrow(A120)+1),] <- c("Chip-17", "226")
A120[(nrow(A120)+1),] <- c("m-07-01", "217")
A120[(nrow(A120)+1),] <- c("m-07-04", "226")
A120[(nrow(A120)+1),] <- c("MS18", "224")
A120[(nrow(A120)+1),] <- c("MS23", "226")
A120[(nrow(A120)+1),] <- c("MS24", "226")
A120[(nrow(A120)+1),] <- c("MS25", "226")
A120[(nrow(A120)+1),] <- c("MS41", "226")
A120[(nrow(A120)+1),] <- c("Pcyph-TN-2", "226")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("ALL14", "224")
A120[(nrow(A120)+1),] <- c("WI95", "226")
# Change incorrect Sample_IDs
A120$Sample_ID <- gsub("CHIP19", "Chip19", A120$Sample_ID)
A120$Sample_ID <- gsub("MS36_536674", "MS36", A120$Sample_ID)
A120$Sample_ID <- gsub("MS42_536676", "MS42", A120$Sample_ID)
A120$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", A120$Sample_ID)
A120$Sample_ID <- gsub("WV1_536678", "WV1", A120$Sample_ID)
A120$Sample_ID <- gsub("MS33_536672", "MS33", A120$Sample_ID)
# Remove duplicates of Chip19, Chip6, MS30, MS34, 16244, MS33
A120 <- A120[-c(119,120),]
A120 <- A120[-c(126),]
A120 <- A120[-c(144,145),]
A120 <- A120[-c(198,199),]
A120 <- A120[-c(209,210),]
A120 <- A120[-c(208),]
A120 <- A120[-c(252,253),]
A120 <- A120[-c(127),]
A120 <- A120[-c(201,202),]
A120 <- A120[-c(267,268),]
# Change ALL6 240 allele to 238
A120[61,2] = 238
# Order spreadsheet
A120 <- A120[order(A120$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
A120_new <- A120 # Create new dataframe 
A120_new$high_low <- rep.int(dummy, nrow(A120_new)/2) # Add extra column delineating high and low alleles
A120_new <- gather(A120_new, key = "loci", value = "genotypes",
                      colnames(A120_new[,-1])) # Gather data
A120_new$high_low <- rep.int(dummy, nrow(A120_new)/2) # Reallocate high and low designations
A120_new <- A120_new[,-c(2)] # Remove loci column
A120_new <- A120_new[-c(301:620),] # Remove doubles? Not sure where they came from
A120_new_wide <- spread(A120_new, high_low, genotypes, fill = 0) # Spread data
names(A120_new_wide) <- c("Sample_ID", "A120_high", "A120_low") # Rename columns

# C1
C1[(nrow(C1)+1),] <- c("Chip-05", "318")
C1[(nrow(C1)+1),] <- c("Chip-11", "314")
C1[(nrow(C1)+1),] <- c("Chip-14", "335")
C1[(nrow(C1)+1),] <- c("m-07-06", "0")
C1[(nrow(C1)+1),] <- c("MS33", "339")
C1[(nrow(C1)+1),] <- c("PMC-2", "286")
C1[(nrow(C1)+1),] <- c("WI92", "362")
C1[(nrow(C1)+1),] <- c("MS32", "339")
# Change incorrect Sample_IDs
C1$C1 <- gsub("OL", "0", C1$C1)
C1$Sample_ID <- gsub("Chip-06", "Chip6", C1$Sample_ID)
C1$Sample_ID <- gsub("Chip-19", "Chip19", C1$Sample_ID)
C1$Sample_ID <- gsub("MS17_535644", "MS17", C1$Sample_ID)
C1$Sample_ID <- gsub("MS25_535645", "MS25", C1$Sample_ID)
C1$Sample_ID <- gsub("MS41_535646", "MS41", C1$Sample_ID)
C1$Sample_ID <- gsub("MS7_535643", "MS7", C1$Sample_ID)
C1$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C1$Sample_ID)
C1$Sample_ID <- gsub("PBH2A_535648", "PBH-2A", C1$Sample_ID)
C1$Sample_ID <- gsub("PBH4A_535647", "PBH-4A", C1$Sample_ID)
C1$Sample_ID <- gsub("TIPP8", "TIPP6", C1$Sample_ID)
# Remove duplicates of ALL11, ALL20, ALL4, MER4, MS6, WV1
C1 <- C1[-c(33,34),]
C1 <- C1[-c(53),]
C1 <- C1[-c(58),]
C1 <- C1[-c(136,137),]
C1 <- C1[-c(222,223),]
C1 <- C1[-c(299:300),]
C1 <- C1[-c(159),]
C1 <- C1[-c(187),]
C1 <- C1[-c(187),]
C1 <- C1[-c(275,276),]
C1 <- C1[-c(275,276),]
C1 <- C1[-c(277,278),]
# Replace 0's with allele calls
C1[11,2] = 289 # 237-1
C1[243,2] = 386 # Pcyph-TN-2
C1[273,2] = 286 # TIPP4
# Replace 339 allele with 335 MS32
C1[187,2] = 335 
C1[188,2] = 335
# Order spreadsheet
C1 <- C1[order(C1$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
C1_new <- C1 # Create new dataframe 
C1_new$high_low <- rep.int(dummy, nrow(C1_new)/2) # Add extra column delineating high and low alleles
C1_new <- gather(C1_new, key = "loci", value = "genotypes",
                      colnames(C1_new[,-1])) # Gather data
C1_new$high_low <- rep.int(dummy, nrow(C1_new)/2) # Reallocate high and low designations
C1_new <- C1_new[,-c(2)] # Remove loci column
C1_new <- C1_new[-c(291:620),] # Remove doubles? Not sure where they came from
C1_new_wide <- spread(C1_new, high_low, genotypes, fill = 0) # Spread data
names(C1_new_wide) <- c("Sample_ID", "C1_high", "C1_low") # Rename columns
C1_new_wide$Sample_ID <- gsub("Chip-06", "Chip6", C1_new_wide$Sample_ID)


# C6
C6[(nrow(C6)+1),] <- c("ALL1", "218")
C6[(nrow(C6)+1),] <- c("ALL17", "213")
C6[(nrow(C6)+1),] <- c("ALL19", "226")
C6[(nrow(C6)+1),] <- c("ALL4", "213")
C6[(nrow(C6)+1),] <- c("Chip-12", "222")
C6[(nrow(C6)+1),] <- c("Chip-13", "218")
C6[(nrow(C6)+1),] <- c("Chip-14", "213")
C6[(nrow(C6)+1),] <- c("Chip-17", "222")
C6[(nrow(C6)+1),] <- c("INHS-14795", "226")
C6[(nrow(C6)+1),] <- c("INHS-25558", "213")
C6[(nrow(C6)+1),] <- c("m-07-01", "218")
C6[(nrow(C6)+1),] <- c("m-07-06", "230")
C6[(nrow(C6)+1),] <- c("MER2", "222")
C6[(nrow(C6)+1),] <- c("Meramec-A", "218")
C6[(nrow(C6)+1),] <- c("Meramec-B", "222")
C6[(nrow(C6)+1),] <- c("MS13", "218")
C6[(nrow(C6)+1),] <- c("MS18", "213")
C6[(nrow(C6)+1),] <- c("MS2", "204")
C6[(nrow(C6)+1),] <- c("MS28", "213")
C6[(nrow(C6)+1),] <- c("MS31", "222")
C6[(nrow(C6)+1),] <- c("MS36", "218")
C6[(nrow(C6)+1),] <- c("Oil-City-A", "204")
C6[(nrow(C6)+1),] <- c("PBH-1A", "176")
C6[(nrow(C6)+1),] <- c("PBH-2A", "176")
C6[(nrow(C6)+1),] <- c("PBH-3A", "176")
C6[(nrow(C6)+1),] <- c("PBH-5A", "209")
C6[(nrow(C6)+1),] <- c("PMC-10", "218")
C6[(nrow(C6)+1),] <- c("PMC-7", "226")
C6[(nrow(C6)+1),] <- c("PMX-4", "218")
C6[(nrow(C6)+1),] <- c("WI92", "218")
C6[(nrow(C6)+1),] <- c("WI92", "218")
C6[(nrow(C6)+1),] <- c("WI95", "218")
# Change incorrect Sample_IDs
C6$Sample_ID <- gsub("CHIP-19", "Chip19", C6$Sample_ID)
C6$Sample_ID <- gsub("MER4", "MER2", C6$Sample_ID)
C6$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP5", "TIPP6", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP6", "TIPP4", C6$Sample_ID)
C6$Sample_ID <- gsub("TIPP7", "TIPP6", C6$Sample_ID)
C6$Sample_ID <- gsub("TN7", "TN8", C6$Sample_ID)
# Remove duplicates
C6 <- C6[-c(15,16),] # 237-2
C6 <- C6[-c(47),] #
C6 <- C6[-c(125,126),] # Chip19
C6 <- C6[-c(157,158),] # m-07-07
C6 <- C6[-c(129),] # 16244
C6 <- C6[-c(149:152),] # m-07-05
# Order spreadsheet
C6 <- C6[order(C6$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
C6_new <- C6 # Create new dataframe 
C6_new$high_low <- rep.int(dummy, nrow(C6_new)/2) # Add extra column delineating high and low alleles
C6_new <- gather(C6_new, key = "loci", value = "genotypes",
                      colnames(C6_new[,-1])) # Gather data
C6_new$high_low <- rep.int(dummy, nrow(C6_new)/2) # Reallocate high and low designations
C6_new <- C6_new[,-c(2)] # Remove loci column
C6_new <- C6_new[-c(313:650),] # Remove doubles? Not sure where they came from
C6_new_wide <- spread(C6_new, high_low, genotypes, fill = 0) # Spread data
names(C6_new_wide) <- c("Sample_ID", "C6_high", "C6_low") # Rename columns

# C105
C105[(nrow(C105)+1),] <- c("ALL14", "272")
C105[(nrow(C105)+1),] <- c("ALL15", "272")
C105[(nrow(C105)+1),] <- c("ALL7", "272")
C105[(nrow(C105)+1),] <- c("C033", "293")
C105[(nrow(C105)+1),] <- c("Chip-08", "283")
C105[(nrow(C105)+1),] <- c("Chip-09", "283")
C105[(nrow(C105)+1),] <- c("INHS-14795", "298")
C105[(nrow(C105)+1),] <- c("m-07-04", "287")
C105[(nrow(C105)+1),] <- c("m-07-07", "300")
C105[(nrow(C105)+1),] <- c("MS17", "310")
C105[(nrow(C105)+1),] <- c("MS31", "291")
C105[(nrow(C105)+1),] <- c("MS44", "310")
C105[(nrow(C105)+1),] <- c("MS5", "287")
C105[(nrow(C105)+1),] <- c("MS8", "287")
C105[(nrow(C105)+1),] <- c("PBH-4A", "295")
C105[(nrow(C105)+1),] <- c("PMC-7", "283")
C105[(nrow(C105)+1),] <- c("MS5", "287")
# Change incorrect Sample_IDs
C105$Sample_ID <- gsub("CHIP19_537805", "Chip19", C105$Sample_ID)
C105$Sample_ID <- gsub("Chip6_537804", "Chip6", C105$Sample_ID)
C105$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C105$Sample_ID)
C105$Sample_ID <- gsub("PBH-2A_537803", "PBH-2A", C105$Sample_ID)
# Remove duplicates
C105 <- C105[-c(97),] # Chip-05
C105 <- C105[-c(127),] # Chip6
C105 <- C105[-c(25),] # A1
C105 <- C105[-c(73),] # BEF-07212-03
C105 <- C105[-c(195:198),] # MS30
C105 <- C105[-c(199:202),] # MS33
C105 <- C105[-c(199:202),] # MS34
C105 <- C105[-c(201:203),] # MS36
C105 <- C105[-c(204),] # MS38
C105 <- C105[-c(213:215),] # MS42
C105 <- C105[-c(237:240),] # PBH-5A
C105 <- C105[-c(287:289),] # WV1
# Order spreadsheet
C105 <- C105[order(C105$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
C105_new <- C105 # Create new dataframe 
C105_new$high_low <- rep.int(dummy, nrow(C105_new)/2) # Add extra column delineating high and low alleles
C105_new <- gather(C105_new, key = "loci", value = "genotypes",
                      colnames(C105_new[,-1])) # Gather data
C105_new$high_low <- rep.int(dummy, nrow(C105_new)/2) # Reallocate high and low designations
C105_new <- C105_new[,-c(2)] # Remove loci column
C105_new <- C105_new[-c(287:650),] # Remove doubles? Not sure where they came from
C105_new_wide <- spread(C105_new, high_low, genotypes, fill = 0) # Spread data
names(C105_new_wide) <- c("Sample_ID", "C105_high", "C105_low") # Rename columns


# C125
C125[(nrow(C125)+1),] <- c("238-4", "253")
C125[(nrow(C125)+1),] <- c("ALL11", "261")
C125[(nrow(C125)+1),] <- c("Chip-02", "249")
C125[(nrow(C125)+1),] <- c("Chip-15", "249")
C125[(nrow(C125)+1),] <- c("Chip-20", "249")
C125[(nrow(C125)+1),] <- c("m-07-06", "264")
C125[(nrow(C125)+1),] <- c("MER2", "257")
C125[(nrow(C125)+1),] <- c("Meramec-B", "249")
C125[(nrow(C125)+1),] <- c("MS1", "245")
C125[(nrow(C125)+1),] <- c("MS13", "253")
C125[(nrow(C125)+1),] <- c("MS16", "249")
C125[(nrow(C125)+1),] <- c("MS19", "249")
C125[(nrow(C125)+1),] <- c("MS26", "249")
C125[(nrow(C125)+1),] <- c("MS31", "249")
C125[(nrow(C125)+1),] <- c("MS33", "249")
C125[(nrow(C125)+1),] <- c("MS34", "264")
C125[(nrow(C125)+1),] <- c("MS37", "245")
C125[(nrow(C125)+1),] <- c("MS38", "249")
C125[(nrow(C125)+1),] <- c("MS44", "249")
C125[(nrow(C125)+1),] <- c("MS7", "232")
C125[(nrow(C125)+1),] <- c("PBH-3A", "227")
C125[(nrow(C125)+1),] <- c("PBH-4A", "249")
C125[(nrow(C125)+1),] <- c("PMC-6", "249")
C125[(nrow(C125)+1),] <- c("PMC-8", "249")
C125[(nrow(C125)+1),] <- c("TIPP4", "264")
# Change incorrect Sample_IDs
C125$Sample_ID <- gsub("CHIP-19", "Chip19", C125$Sample_ID)
C125$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", C125$Sample_ID)
C125$Sample_ID <- gsub("TN2", "Pcyph-TN-2", C125$Sample_ID)
# Order spreadsheet
C125 <- C125[order(C125$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
C125_new <- C125 # Create new dataframe 
C125_new$high_low <- rep.int(dummy, nrow(C125_new)/2) # Add extra column delineating high and low alleles
C125_new <- gather(C125_new, key = "loci", value = "genotypes",
                      colnames(C125_new[,-1])) # Gather data
C125_new$high_low <- rep.int(dummy, nrow(C125_new)/2) # Reallocate high and low designations
C125_new <- C125_new[,-c(2)] # Remove loci column
C125_new <- C125_new[-c(295:650),] # Remove doubles? Not sure where they came from
C125_new_wide <- spread(C125_new, high_low, genotypes, fill = 0) # Spread data
names(C125_new_wide) <- c("Sample_ID", "C125_high", "C125_low") # Rename columns


# D4
D4[(nrow(D4)+1),] <- c("ALL16", "273")
D4[(nrow(D4)+1),] <- c("ALL19", "281")
D4[(nrow(D4)+1),] <- c("ALL6", "273")
D4[(nrow(D4)+1),] <- c("Chip-10", "297")
D4[(nrow(D4)+1),] <- c("Chip-15", "297")
D4[(nrow(D4)+1),] <- c("INHS-22893", "297")
D4[(nrow(D4)+1),] <- c("INHS-30476", "273")
D4[(nrow(D4)+1),] <- c("m-07-04", "285")
D4[(nrow(D4)+1),] <- c("MER2", "313")
D4[(nrow(D4)+1),] <- c("MS21", "242")
D4[(nrow(D4)+1),] <- c("MS27", "270")
D4[(nrow(D4)+1),] <- c("MS29", "242")
D4[(nrow(D4)+1),] <- c("MS3", "317")
D4[(nrow(D4)+1),] <- c("MS5", "273")
D4[(nrow(D4)+1),] <- c("PMC-10", "289")
D4[(nrow(D4)+1),] <- c("PMC-8", "289")
D4[(nrow(D4)+1),] <- c("PMC-9", "270")
D4[(nrow(D4)+1),] <- c("MS27", "270")
D4[(nrow(D4)+1),] <- c("MS27", "270")
# Change incorrect Sample_IDs
D4$Sample_ID <- gsub("CHIP19", "Chip19", D4$Sample_ID)
D4$Sample_ID <- gsub("MER4", "MER2", D4$Sample_ID)
D4$Sample_ID <- gsub("MS3_536151", "MS3", D4$Sample_ID)
D4$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D4$Sample_ID)
D4$Sample_ID <- gsub("TIPP5", "TIPP4", D4$Sample_ID)
D4$Sample_ID <- gsub("TIPP8", "TIPP6", D4$Sample_ID)
D4$Sample_ID <- gsub("TN7", "TN8", D4$Sample_ID)
D4$Sample_ID <- gsub("PBH4A", "PBH-4A", D4$Sample_ID)
# Remove duplicates
D4 <- D4[-c(43,44),] # ALL15
D4 <- D4[-c(55:59),] # ALL20
D4 <- D4[-c(65,66),] # ALL7
D4 <- D4[-c(125,126),] # Chip19
D4 <- D4[-c(127,128),] # Chip6
D4 <- D4[-c(165,166),] # MS16
D4 <- D4[-c(313:318),] # MS16
D4 <- D4[-c(165:168),] # MS17
D4 <- D4[-c(181:183),] # MS25
D4 <- D4[-c(215:218),] # MS41
D4 <- D4[-c(226:229),] # MS7
D4 <- D4[-c(223:225),] # MS6
D4 <- D4[-c(237:240),] # PBH-4A
# Order spreadsheet
D4 <- D4[order(D4$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D4_new <- D4 # Create new dataframe 
D4_new$high_low <- rep.int(dummy, nrow(D4_new)/2) # Add extra column delineating high and low alleles
D4_new <- gather(D4_new, key = "loci", value = "genotypes",
                      colnames(D4_new[,-1])) # Gather data
D4_new$high_low <- rep.int(dummy, nrow(D4_new)/2) # Reallocate high and low designations
D4_new <- D4_new[,-c(2)] # Remove loci column
D4_new <- D4_new[-c(291:650),] # Remove doubles? Not sure where they came from
D4_new_wide <- spread(D4_new, high_low, genotypes, fill = 0) # Spread data
names(D4_new_wide) <- c("Sample_ID", "D4_high", "D4_low") # Rename columns


# D10
D10[(nrow(D10)+1),] <- c("130-1", "201")
D10[(nrow(D10)+1),] <- c("130-3", "201")
D10[(nrow(D10)+1),] <- c("236-1", "201")
D10[(nrow(D10)+1),] <- c("236-2", "201")
D10[(nrow(D10)+1),] <- c("237-3", "201")
D10[(nrow(D10)+1),] <- c("238-1", "201")
D10[(nrow(D10)+1),] <- c("238-2", "201")
D10[(nrow(D10)+1),] <- c("238-4", "201")
D10[(nrow(D10)+1),] <- c("A2", "206")
D10[(nrow(D10)+1),] <- c("ALL1", "201")
D10[(nrow(D10)+1),] <- c("ALL10", "201")
D10[(nrow(D10)+1),] <- c("ALL11", "201")
D10[(nrow(D10)+1),] <- c("ALL12", "201")
D10[(nrow(D10)+1),] <- c("ALL13", "201")
D10[(nrow(D10)+1),] <- c("ALL14", "201")
D10[(nrow(D10)+1),] <- c("ALL15", "201")
D10[(nrow(D10)+1),] <- c("ALL16", "201")
D10[(nrow(D10)+1),] <- c("ALL17", "201")
D10[(nrow(D10)+1),] <- c("ALL18", "201")
D10[(nrow(D10)+1),] <- c("ALL19", "201")
D10[(nrow(D10)+1),] <- c("ALL2", "201")
D10[(nrow(D10)+1),] <- c("ALL20", "201")
D10[(nrow(D10)+1),] <- c("ALL3", "201")
D10[(nrow(D10)+1),] <- c("ALL4", "201")
D10[(nrow(D10)+1),] <- c("ALL5", "201")
D10[(nrow(D10)+1),] <- c("ALL6", "201")
D10[(nrow(D10)+1),] <- c("ALL7", "201")
D10[(nrow(D10)+1),] <- c("ALL8", "201")
D10[(nrow(D10)+1),] <- c("ALL9", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-01", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-02", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-03", "201")
D10[(nrow(D10)+1),] <- c("BEF-07212-05", "201")
D10[(nrow(D10)+1),] <- c("C024", "197")
D10[(nrow(D10)+1),] <- c("C041", "197")
D10[(nrow(D10)+1),] <- c("C219", "197")
D10[(nrow(D10)+1),] <- c("Chip-07", "201")
D10[(nrow(D10)+1),] <- c("Chip-12", "232")
D10[(nrow(D10)+1),] <- c("Chip-13", "232")
D10[(nrow(D10)+1),] <- c("Chip-16", "201")
D10[(nrow(D10)+1),] <- c("INHS-3531", "197")
D10[(nrow(D10)+1),] <- c("MS10", "232")
D10[(nrow(D10)+1),] <- c("MS16", "206")
D10[(nrow(D10)+1),] <- c("MS17", "206")
D10[(nrow(D10)+1),] <- c("MS20", "206")
D10[(nrow(D10)+1),] <- c("MS26", "206")
D10[(nrow(D10)+1),] <- c("MS27", "206")
D10[(nrow(D10)+1),] <- c("MS29", "201")
D10[(nrow(D10)+1),] <- c("MS30", "201")
D10[(nrow(D10)+1),] <- c("MS31", "201")
D10[(nrow(D10)+1),] <- c("MS33", "201")
D10[(nrow(D10)+1),] <- c("MS38", "201")
D10[(nrow(D10)+1),] <- c("MS43", "201")
D10[(nrow(D10)+1),] <- c("MS44", "194")
D10[(nrow(D10)+1),] <- c("MS5", "206")
D10[(nrow(D10)+1),] <- c("MS7", "206")
D10[(nrow(D10)+1),] <- c("Oil-City-A", "201")
D10[(nrow(D10)+1),] <- c("Oil-City-B", "201")
D10[(nrow(D10)+1),] <- c("PBH-1A", "201")
D10[(nrow(D10)+1),] <- c("PBH-2A", "201")
D10[(nrow(D10)+1),] <- c("PBH-3A", "201")
D10[(nrow(D10)+1),] <- c("PBH-4A", "232")
D10[(nrow(D10)+1),] <- c("Pcyph-TN-1", "197")
D10[(nrow(D10)+1),] <- c("PMC-1", "228")
D10[(nrow(D10)+1),] <- c("PMC-5", "241")
D10[(nrow(D10)+1),] <- c("PMC-7", "232")
D10[(nrow(D10)+1),] <- c("PMC-8", "232")
D10[(nrow(D10)+1),] <- c("PMX-2", "232")
D10[(nrow(D10)+1),] <- c("TIPP4", "201")
D10[(nrow(D10)+1),] <- c("TIPP6", "201")
D10[(nrow(D10)+1),] <- c("Pcyph-TN-2", "197")
D10[(nrow(D10)+1),] <- c("TN8", "197")
D10[(nrow(D10)+1),] <- c("UAUC3157", "197")
D10[(nrow(D10)+1),] <- c("WI95", "232")
D10[(nrow(D10)+1),] <- c("WV1", "201")
# Change incorrect Sample_IDs
D10$Sample_ID <- gsub("CHIP-19", "Chip19", D10$Sample_ID)
D10$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D10$Sample_ID)
D10$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D10$Sample_ID)
# Remove duplicates
D10 <- D10[-c(90),] # Chip-05
D10 <- D10[-c(269,270),] # PMC-3
D10 <- D10[-c(294),] # TIPP6
D10 <- D10[-c(127:129),] # INHS-14795
D10 <- D10[-c(133:135),] # INHS-6271
D10 <- D10[-c(305),] # 130-1
# Order spreadsheet
D10 <- D10[order(D10$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D10_new <- D10 # Create new dataframe 
D10_new$high_low <- rep.int(dummy, nrow(D10_new)/2) # Add extra column delineating high and low alleles
D10_new <- gather(D10_new, key = "loci", value = "genotypes",
                      colnames(D10_new[,-1])) # Gather data
D10_new$high_low <- rep.int(dummy, nrow(D10_new)/2) # Reallocate high and low designations
D10_new <- D10_new[,-c(2)] # Remove loci column
D10_new <- D10_new[-c(305:650),] # Remove doubles? Not sure where they came from
D10_new_wide <- spread(D10_new, high_low, genotypes, fill = 0) # Spread data
names(D10_new_wide) <- c("Sample_ID", "D10_high", "D10_low") # Rename columns


# D106
D106[(nrow(D106)+1),] <- c("236-1", "272")
D106[(nrow(D106)+1),] <- c("237-1", "272")
D106[(nrow(D106)+1),] <- c("ALL14", "280")
D106[(nrow(D106)+1),] <- c("ALL15", "291")
D106[(nrow(D106)+1),] <- c("ALL18", "291")
D106[(nrow(D106)+1),] <- c("ALL3", "260")
D106[(nrow(D106)+1),] <- c("ALL6", "280")
D106[(nrow(D106)+1),] <- c("ALL8", "256")
D106[(nrow(D106)+1),] <- c("ALL9", "272")
D106[(nrow(D106)+1),] <- c("BEF-07212-02", "276")
D106[(nrow(D106)+1),] <- c("BEF-07212-05", "254")
D106[(nrow(D106)+1),] <- c("Chip-02", "260")
D106[(nrow(D106)+1),] <- c("Chip-07", "291")
D106[(nrow(D106)+1),] <- c("Chip-11", "291")
D106[(nrow(D106)+1),] <- c("Chip-15", "284")
D106[(nrow(D106)+1),] <- c("Chip-16", "272")
D106[(nrow(D106)+1),] <- c("m-07-04", "284")
D106[(nrow(D106)+1),] <- c("MS1", "276")
D106[(nrow(D106)+1),] <- c("MS12", "284")
D106[(nrow(D106)+1),] <- c("MS13", "284")
D106[(nrow(D106)+1),] <- c("MS14", "284")
D106[(nrow(D106)+1),] <- c("MS17", "294")
D106[(nrow(D106)+1),] <- c("MS18", "276")
D106[(nrow(D106)+1),] <- c("MS20", "260")
D106[(nrow(D106)+1),] <- c("MS27", "260")
D106[(nrow(D106)+1),] <- c("MS28", "256")
D106[(nrow(D106)+1),] <- c("MS31", "280")
D106[(nrow(D106)+1),] <- c("MS40", "284")
D106[(nrow(D106)+1),] <- c("PBH-2A", "242")
D106[(nrow(D106)+1),] <- c("PBH-3A", "242")
D106[(nrow(D106)+1),] <- c("PBH-4A", "276")
D106[(nrow(D106)+1),] <- c("PMC-9", "276")
D106[(nrow(D106)+1),] <- c("WI92", "280")
D106[(nrow(D106)+1),] <- c("WI94", "284")
# Change incorrect Sample_IDs
D106$Sample_ID <- gsub("CHIP-19", "Chip19", D106$Sample_ID)
D106$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D106$Sample_ID)
D106$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D106$Sample_ID)
# Remove duplicates
D106 <- D106[-c(150),] # MS13
D106 <- D106[-c(9),] # 236-1
# Order spreadsheet
D106 <- D106[order(D106$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D106_new <- D106 # Create new dataframe 
D106_new$high_low <- rep.int(dummy, nrow(D106_new)/2) # Add extra column delineating high and low alleles
D106_new <- gather(D106_new, key = "loci", value = "genotypes",
                      colnames(D106_new[,-1])) # Gather data
D106_new$high_low <- rep.int(dummy, nrow(D106_new)/2) # Reallocate high and low designations
D106_new <- D106_new[,-c(2)] # Remove loci column
D106_new <- D106_new[-c(293:650),] # Remove doubles? Not sure where they came from
D106_new_wide <- spread(D106_new, high_low, genotypes, fill = 0) # Spread data
names(D106_new_wide) <- c("Sample_ID", "D106_high", "D106_low") # Rename columns

# D113
D113[(nrow(D113)+1),] <- c("236-1", "274")
D113[(nrow(D113)+1),] <- c("236-2", "289")
D113[(nrow(D113)+1),] <- c("237-1", "572")
D113[(nrow(D113)+1),] <- c("237-2", "289")
D113[(nrow(D113)+1),] <- c("238-3", "281")
D113[(nrow(D113)+1),] <- c("238-4", "289")
D113[(nrow(D113)+1),] <- c("A2", "296")
D113[(nrow(D113)+1),] <- c("ALL11", "281")
D113[(nrow(D113)+1),] <- c("ALL12", "277")
D113[(nrow(D113)+1),] <- c("ALL14", "277")
D113[(nrow(D113)+1),] <- c("ALL15", "281")
D113[(nrow(D113)+1),] <- c("ALL17", "269")
D113[(nrow(D113)+1),] <- c("ALL18", "289")
D113[(nrow(D113)+1),] <- c("ALL6", "296")
D113[(nrow(D113)+1),] <- c("ALL7", "296")
D113[(nrow(D113)+1),] <- c("BEF-07212-01", "484")
D113[(nrow(D113)+1),] <- c("C024", "300")
D113[(nrow(D113)+1),] <- c("C033", "285")
D113[(nrow(D113)+1),] <- c("Chip-05", "296")
D113[(nrow(D113)+1),] <- c("Chip-11", "296")
D113[(nrow(D113)+1),] <- c("Chip-12", "296")
D113[(nrow(D113)+1),] <- c("Chip-13", "296")
D113[(nrow(D113)+1),] <- c("Chip-20", "296")
D113[(nrow(D113)+1),] <- c("INHS-16244", "296")
D113[(nrow(D113)+1),] <- c("INHS-25558", "296")
D113[(nrow(D113)+1),] <- c("INHS-3531", "277")
D113[(nrow(D113)+1),] <- c("INHS-6271", "277")
D113[(nrow(D113)+1),] <- c("m-07-05", "376")
D113[(nrow(D113)+1),] <- c("Meramec-A", "399")
D113[(nrow(D113)+1),] <- c("Meramec-B", "407")
D113[(nrow(D113)+1),] <- c("MS1", "300")
D113[(nrow(D113)+1),] <- c("MS10", "296")
D113[(nrow(D113)+1),] <- c("MS13", "296")
D113[(nrow(D113)+1),] <- c("MS14", "300")
D113[(nrow(D113)+1),] <- c("MS16", "296")
D113[(nrow(D113)+1),] <- c("MS18", "296")
D113[(nrow(D113)+1),] <- c("MS23", "296")
D113[(nrow(D113)+1),] <- c("MS26", "300")
D113[(nrow(D113)+1),] <- c("MS27", "296")
D113[(nrow(D113)+1),] <- c("MS3", "296")
D113[(nrow(D113)+1),] <- c("MS31", "296")
D113[(nrow(D113)+1),] <- c("MS32", "296")
D113[(nrow(D113)+1),] <- c("MS4", "296")
D113[(nrow(D113)+1),] <- c("MS42", "296")
D113[(nrow(D113)+1),] <- c("MS43", "296")
D113[(nrow(D113)+1),] <- c("MS5", "296")
D113[(nrow(D113)+1),] <- c("MS6", "296")
D113[(nrow(D113)+1),] <- c("MS8", "296")
D113[(nrow(D113)+1),] <- c("MS9", "296")
D113[(nrow(D113)+1),] <- c("Oil-City-A", "325")
D113[(nrow(D113)+1),] <- c("Oil-City-B", "293")
D113[(nrow(D113)+1),] <- c("PBH-3A", "321")
D113[(nrow(D113)+1),] <- c("PMC-10", "380")
D113[(nrow(D113)+1),] <- c("PMC-2", "321")
D113[(nrow(D113)+1),] <- c("PMC-3", "346")
D113[(nrow(D113)+1),] <- c("PMC-6", "325")
D113[(nrow(D113)+1),] <- c("PMC-7", "403")
D113[(nrow(D113)+1),] <- c("PMC-8", "321")
D113[(nrow(D113)+1),] <- c("PMC-9", "317")
D113[(nrow(D113)+1),] <- c("PMX-1", "317")
D113[(nrow(D113)+1),] <- c("WI92", "300")
D113[(nrow(D113)+1),] <- c("WV1", "277")
# Change incorrect Sample_IDs
D113$Sample_ID <- gsub("CHIP-19", "Chip19", D113$Sample_ID)
D113$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D113$Sample_ID)
D113$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D113$Sample_ID)
# Remove duplicates
D113 <- D113[-c(209,210),] # MS33
D113 <- D113[-c(211,212),] # MS34
D113 <- D113[-c(287,288),] # TIPP4
D113 <- D113[-c(291,292),] # Pcyph-TN-2
D113 <- D113[-c(293,294),] # TN8
D113 <- D113[-c(135:137),] # INHS-9470
# Order spreadsheet
D113 <- D113[order(D113$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D113_new <- D113 # Create new dataframe 
D113_new$high_low <- rep.int(dummy, nrow(D113_new)/2) # Add extra column delineating high and low alleles
D113_new <- gather(D113_new, key = "loci", value = "genotypes",
                      colnames(D113_new[,-1])) # Gather data
D113_new$high_low <- rep.int(dummy, nrow(D113_new)/2) # Reallocate high and low designations
D113_new <- D113_new[,-c(2)] # Remove loci column
D113_new <- D113_new[-c(303:650),] # Remove doubles? Not sure where they came from
D113_new_wide <- spread(D113_new, high_low, genotypes, fill = 0) # Spread data
names(D113_new_wide) <- c("Sample_ID", "D113_high", "D113_low") # Rename columns

# D114
D114[(nrow(D114)+1),] <- c("ALL12", "244")
D114[(nrow(D114)+1),] <- c("ALL16", "244")
D114[(nrow(D114)+1),] <- c("ALL8", "244")
D114[(nrow(D114)+1),] <- c("BEF-07212-01", "244")
D114[(nrow(D114)+1),] <- c("Chip-07", "244")
D114[(nrow(D114)+1),] <- c("Chip-09", "244")
D114[(nrow(D114)+1),] <- c("Chip-11", "244")
D114[(nrow(D114)+1),] <- c("Chip-13", "244")
D114[(nrow(D114)+1),] <- c("Chip-15", "244")
D114[(nrow(D114)+1),] <- c("Chip-17", "244")
D114[(nrow(D114)+1),] <- c("Chip-18", "240")
D114[(nrow(D114)+1),] <- c("Chip6", "244")
D114[(nrow(D114)+1),] <- c("INHS-16244", "244")
D114[(nrow(D114)+1),] <- c("INHS-3531", "244")
D114[(nrow(D114)+1),] <- c("m-07-06", "249")
D114[(nrow(D114)+1),] <- c("Meramec-B", "240")
D114[(nrow(D114)+1),] <- c("MS10", "240")
D114[(nrow(D114)+1),] <- c("MS13", "244")
D114[(nrow(D114)+1),] <- c("MS19", "244")
D114[(nrow(D114)+1),] <- c("MS27", "244")
D114[(nrow(D114)+1),] <- c("MS30", "240")
D114[(nrow(D114)+1),] <- c("MS5", "244")
D114[(nrow(D114)+1),] <- c("Oil-City-A", "261")
D114[(nrow(D114)+1),] <- c("Oil-City-B", "244")
D114[(nrow(D114)+1),] <- c("PBH-1A", "254")
D114[(nrow(D114)+1),] <- c("PBH-3A", "254")
D114[(nrow(D114)+1),] <- c("Pcyph-TN-1", "244")
D114[(nrow(D114)+1),] <- c("PMC-2", "240")
D114[(nrow(D114)+1),] <- c("PMC-3", "236")
D114[(nrow(D114)+1),] <- c("PMX-3", "249")
D114[(nrow(D114)+1),] <- c("Pcyph-TN-2", "236")
D114[(nrow(D114)+1),] <- c("WI92", "249")
# Change incorrect Sample_IDs
D114$Sample_ID <- gsub("CHIP-19", "Chip19", D114$Sample_ID)
D114$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D114$Sample_ID)
D114$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D114$Sample_ID)
# Remove duplicates
D114 <- D114[-c(94),] # Chip-05
D114 <- D114[-c(149),] # m-07-07
D114 <- D114[-c(135:137),] # INHS-6271
# Order spreadsheet
D114 <- D114[order(D114$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D114_new <- D114 # Create new dataframe 
D114_new$high_low <- rep.int(dummy, nrow(D114_new)/2) # Add extra column delineating high and low alleles
D114_new <- gather(D114_new, key = "loci", value = "genotypes",
                      colnames(D114_new[,-1])) # Gather data
D114_new$high_low <- rep.int(dummy, nrow(D114_new)/2) # Reallocate high and low designations
D114_new <- D114_new[,-c(2)] # Remove loci column
D114_new <- D114_new[-c(307:650),] # Remove doubles? Not sure where they came from
D114_new_wide <- spread(D114_new, high_low, genotypes, fill = 0) # Spread data
names(D114_new_wide) <- c("Sample_ID", "D114_high", "D114_low") # Rename columns

# D119
D119[(nrow(D119)+1),] <- c("130-3", "298")
D119[(nrow(D119)+1),] <- c("238-1", "306")
D119[(nrow(D119)+1),] <- c("ALL10", "302")
D119[(nrow(D119)+1),] <- c("ALL12", "327")
D119[(nrow(D119)+1),] <- c("ALL12", "244")
D119[(nrow(D119)+1),] <- c("ALL2", "298")
D119[(nrow(D119)+1),] <- c("ALL3", "294")
D119[(nrow(D119)+1),] <- c("BEF-07212-05", "302")
D119[(nrow(D119)+1),] <- c("Chip-08", "306")
D119[(nrow(D119)+1),] <- c("Chip-12", "298")
D119[(nrow(D119)+1),] <- c("Chip-20", "306")
D119[(nrow(D119)+1),] <- c("MS18", "302")
D119[(nrow(D119)+1),] <- c("MS20", "306")
D119[(nrow(D119)+1),] <- c("MS23", "310")
D119[(nrow(D119)+1),] <- c("MS25", "310")
D119[(nrow(D119)+1),] <- c("MS29", "310")
D119[(nrow(D119)+1),] <- c("MS33", "302")
D119[(nrow(D119)+1),] <- c("MS42", "302")
D119[(nrow(D119)+1),] <- c("PBH-1A", "332")
D119[(nrow(D119)+1),] <- c("PMC-2", "306")
D119[(nrow(D119)+1),] <- c("PMC-8", "298")
D119[(nrow(D119)+1),] <- c("PMX-5", "302")
D119[(nrow(D119)+1),] <- c("WV1", "306")
# Change incorrect Sample_IDs
D119$Sample_ID <- gsub("CHIP-19", "Chip19", D119$Sample_ID)
D119$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D119$Sample_ID)
D119$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D119$Sample_ID)
# Order spreadsheet
D119 <- D119[order(D119$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D119_new <- D119 # Create new dataframe 
D119_new$high_low <- rep.int(dummy, nrow(D119_new)/2) # Add extra column delineating high and low alleles
D119_new <- gather(D119_new, key = "loci", value = "genotypes",
                      colnames(D119_new[,-1])) # Gather data
D119_new$high_low <- rep.int(dummy, nrow(D119_new)/2) # Reallocate high and low designations
D119_new <- D119_new[,-c(2)] # Remove loci column
D119_new <- D119_new[-c(297:650),] # Remove doubles? Not sure where they came from
D119_new_wide <- spread(D119_new, high_low, genotypes, fill = 0) # Spread data
names(D119_new_wide) <- c("Sample_ID", "D119_high", "D119_low") # Rename columns

# D125
D125[(nrow(D125)+1),] <- c("130-1", "278")
D125[(nrow(D125)+1),] <- c("236-2", "260")
D125[(nrow(D125)+1),] <- c("Chip-03", "249")
D125[(nrow(D125)+1),] <- c("Chip-10", "245")
D125[(nrow(D125)+1),] <- c("Chip-11", "264")
D125[(nrow(D125)+1),] <- c("Chip-14", "278")
D125[(nrow(D125)+1),] <- c("Chip-16", "241")
D125[(nrow(D125)+1),] <- c("INHS-6271", "252")
D125[(nrow(D125)+1),] <- c("m-07-03", "271")
D125[(nrow(D125)+1),] <- c("m-07-06", "256")
D125[(nrow(D125)+1),] <- c("MS14", "256")
D125[(nrow(D125)+1),] <- c("MS22", "260")
D125[(nrow(D125)+1),] <- c("MS29", "256")
D125[(nrow(D125)+1),] <- c("MS3", "252")
D125[(nrow(D125)+1),] <- c("MS9", "274")
D125[(nrow(D125)+1),] <- c("Oil-City-A", "267")
D125[(nrow(D125)+1),] <- c("PMC-8", "267")
D125[(nrow(D125)+1),] <- c("UAUC3157", "245")
D125[(nrow(D125)+1),] <- c("WI93", "249")
# Change incorrect Sample_IDs
D125$Sample_ID <- gsub("CHIP-19", "Chip19", D125$Sample_ID)
D125$Sample_ID <- gsub("Oil-City-B-", "Oil-City-B", D125$Sample_ID)
D125$Sample_ID <- gsub("TN2", "Pcyph-TN-2", D125$Sample_ID)
# Remove duplicates
D125 <- D125[-c(145:147),] # m-07-07
D125 <- D125[-c(147),] # m-07-07
D125 <- D125[-c(93:96),] # Chip-05
D125 <- D125[-c(275:280),] # PMX-2
# Order spreadsheet
D125 <- D125[order(D125$Sample_ID),]
#Spread data
dummy <- c("high", "low") # Create dummy vector
D125_new <- D125 # Create new dataframe 
D125_new$high_low <- rep.int(dummy, nrow(D125_new)/2) # Add extra column delineating high and low alleles
D125_new <- gather(D125_new, key = "loci", value = "genotypes",
                      colnames(D125_new[,-1])) # Gather data
D125_new$high_low <- rep.int(dummy, nrow(D125_new)/2) # Reallocate high and low designations
D125_new <- D125_new[,-c(2)] # Remove loci column
D125_new <- D125_new[-c(299:650),] # Remove doubles? Not sure where they came from
D125_new_wide <- spread(D125_new, high_low, genotypes, fill = 0) # Spread data
names(D125_new_wide) <- c("Sample_ID", "D125_high", "D125_low") # Rename columns
```


# Add duplicate row for second homozygous allele and spread data of Wisconsin samples
```{r}
## Must be done by locus
# A103_wis
A103_wis[(nrow(A103_wis)+1),] <- c("PCP2", "251")
A103_wis[(nrow(A103_wis)+1),] <- c("PWO5", "249")
# Order data
A103_wis <- A103_wis[order(A103_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
A103new <- A103_wis # Create new dataframe 
A103new$high_low <- rep.int(dummy, nrow(A103new)/2) # Add extra column delineating high and low alleles
A103new <- gather(A103new, key = "loci", value = "genotypes",
                      colnames(A103new[,-1])) # Gather data
A103new$high_low <- rep.int(dummy, nrow(A103new)/2) # Reallocate high and low designations
A103new <- A103new[,-c(2)] # Remove loci column
A103new <- A103new[-c(25:48),] # Remove doubles? Not sure where they came from
A103new_wide <- spread(A103new, high_low, genotypes, fill = 0) # Spread data
names(A103new_wide) <- c("Sample_ID", "A103_high", "A103_low") # Rename columns


# A115_wis
A115_wis[(nrow(A115_wis)+1),] <- c("PWO10", "299")
A115_wis[(nrow(A115_wis)+1),] <- c("PWO3", "289")
# Order data
A115_wis <- A115_wis[order(A115_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
A115new <- A115_wis # Create new dataframe 
A115new$high_low <- rep.int(dummy, nrow(A115new)/2) # Add extra column delineating high and low alleles
A115new <- gather(A115new, key = "loci", value = "genotypes",
                      colnames(A115new[,-1])) # Gather data
A115new$high_low <- rep.int(dummy, nrow(A115new)/2) # Reallocate high and low designations
A115new <- A115new[,-c(2)] # Remove loci column
A115new <- A115new[-c(23:48),] # Remove doubles? Not sure where they came from
A115new_wide <- spread(A115new, high_low, genotypes, fill = 0) # Spread data
names(A115new_wide) <- c("Sample_ID", "A115_high", "A115_low") # Rename columns

# A120_wis
A120_wis[(nrow(A120_wis)+1),] <- c("PCP1", "226")
A120_wis[(nrow(A120_wis)+1),] <- c("PCP2", "226")
A120_wis[(nrow(A120_wis)+1),] <- c("PWO10", "226")
# Order data
A120_wis <- A120_wis[order(A120_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
A120new <- A120_wis # Create new dataframe 
A120new$high_low <- rep.int(dummy, nrow(A120new)/2) # Add extra column delineating high and low alleles
A120new <- gather(A120new, key = "loci", value = "genotypes",
                      colnames(A120new[,-1])) # Gather data
A120new$high_low <- rep.int(dummy, nrow(A120new)/2) # Reallocate high and low designations
A120new <- A120new[,-c(2)] # Remove loci column
A120new <- A120new[-c(19:48),] # Remove doubles? Not sure where they came from
A120new_wide <- spread(A120new, high_low, genotypes, fill = 0) # Spread data
names(A120new_wide) <- c("Sample_ID", "A120_high", "A120_low") # Rename columns


# C1_wis
C1_wis[(nrow(C1_wis)+1),] <- c("PCP1", "331")
C1_wis[(nrow(C1_wis)+1),] <- c("PCP2", "339")
C1_wis[(nrow(C1_wis)+1),] <- c("PWO3", "335")
# Order data
C1_wis <- C1_wis[order(C1_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
C1new <- C1_wis # Create new dataframe 
C1new$high_low <- rep.int(dummy, nrow(C1new)/2) # Add extra column delineating high and low alleles
C1new <- gather(C1new, key = "loci", value = "genotypes",
                      colnames(C1new[,-1])) # Gather data
C1new$high_low <- rep.int(dummy, nrow(C1new)/2) # Reallocate high and low designations
C1new <- C1new[,-c(2)] # Remove loci column
C1new <- C1new[-c(25:48),] # Remove doubles? Not sure where they came from
C1new_wide <- spread(C1new, high_low, genotypes, fill = 0) # Spread data
names(C1new_wide) <- c("Sample_ID", "C1_high", "C1_low") # Rename columns


# C6_wis
C6_wis[(nrow(C6_wis)+1),] <- c("PCP1", "218")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO1", "213")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO3", "213")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO5", "218")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO6", "213")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO7", "218")
C6_wis[(nrow(C6_wis)+1),] <- c("PWO9", "218")
# Order data
C6_wis <- C6_wis[order(C6_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
C6new <- C6_wis # Create new dataframe 
C6new$high_low <- rep.int(dummy, nrow(C6new)/2) # Add extra column delineating high and low alleles
C6new <- gather(C6new, key = "loci", value = "genotypes",
                      colnames(C6new[,-1])) # Gather data
C6new$high_low <- rep.int(dummy, nrow(C6new)/2) # Reallocate high and low designations
C6new <- C6new[,-c(2)] # Remove loci column
C6new <- C6new[-c(25:48),] # Remove doubles? Not sure where they came from
C6new_wide <- spread(C6new, high_low, genotypes, fill = 0) # Spread data
names(C6new_wide) <- c("Sample_ID", "C6_high", "C6_low") # Rename columns


# C105_wis
C105_wis[(nrow(C105_wis)+1),] <- c("PWO10", "283")
# Order data
C105_wis <- C105_wis[order(C105_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
C105new <- C105_wis # Create new dataframe 
C105new$high_low <- rep.int(dummy, nrow(C105new)/2) # Add extra column delineating high and low alleles
C105new <- gather(C105new, key = "loci", value = "genotypes",
                      colnames(C105new[,-1])) # Gather data
C105new$high_low <- rep.int(dummy, nrow(C105new)/2) # Reallocate high and low designations
C105new <- C105new[,-c(2)] # Remove loci column
C105new <- C105new[-c(25:48),] # Remove doubles? Not sure where they came from
C105new_wide <- spread(C105new, high_low, genotypes, fill = 0) # Spread data
names(C105new_wide) <- c("Sample_ID", "C105_high", "C105_low") # Rename column


# C125_wis
C125_wis[(nrow(C125_wis)+1),] <- c("PWO3", "249")
C125_wis[(nrow(C125_wis)+1),] <- c("PWO6", "268")
# Order data
C125_wis <- C125_wis[order(C125_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
C125new <- C125_wis # Create new dataframe 
C125new$high_low <- rep.int(dummy, nrow(C125new)/2) # Add extra column delineating high and low alleles
C125new <- gather(C125new, key = "loci", value = "genotypes",
                      colnames(C125new[,-1])) # Gather data
C125new$high_low <- rep.int(dummy, nrow(C125new)/2) # Reallocate high and low designations
C125new <- C125new[,-c(2)] # Remove loci column
C125new <- C125new[-c(25:48),] # Remove doubles? Not sure where they came from
C125new_wide <- spread(C125new, high_low, genotypes, fill = 0) # Spread data
names(C125new_wide) <- c("Sample_ID", "C125_high", "C125_low") # Rename column


# D4_wis
D4_wis[(nrow(D4_wis)+1),] <- c("PWO10", "283")
# Order data
D4_wis <- D4_wis[order(D4_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D4new <- D4_wis # Create new dataframe 
D4new$high_low <- rep.int(dummy, nrow(D4new)/2) # Add extra column delineating high and low alleles
D4new <- gather(D4new, key = "loci", value = "genotypes",
                      colnames(D4new[,-1])) # Gather data
D4new$high_low <- rep.int(dummy, nrow(D4new)/2) # Reallocate high and low designations
D4new <- D4new[,-c(2)] # Remove loci column
D4new <- D4new[-c(25:48),] # Remove doubles? Not sure where they came from
D4new_wide <- spread(D4new, high_low, genotypes, fill = 0) # Spread data
names(D4new_wide) <- c("Sample_ID", "D4_high", "D4_low") # Rename column


# D10_wis
D10_wis[(nrow(D10_wis)+1),] <- c("PWO3", "194")
D10_wis[(nrow(D10_wis)+1),] <- c("PWO9", "232")
# Order data
D10_wis <- D10_wis[order(D10_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D10new <- D10_wis # Create new dataframe 
D10new$high_low <- rep.int(dummy, nrow(D10new)/2) # Add extra column delineating high and low alleles
D10new <- gather(D10new, key = "loci", value = "genotypes",
                      colnames(D10new[,-1])) # Gather data
D10new$high_low <- rep.int(dummy, nrow(D10new)/2) # Reallocate high and low designations
D10new <- D10new[,-c(2)] # Remove loci column
D10new <- D10new[-c(25:48),] # Remove doubles? Not sure where they came from
D10new_wide <- spread(D10new, high_low, genotypes, fill = 0) # Spread data
names(D10new_wide) <- c("Sample_ID", "D10_high", "D10_low") # Rename column


# D106_wis
D106_wis[(nrow(D106_wis)+1),] <- c("PWO1", "284")
# Order data
D106_wis <- D106_wis[order(D106_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D106new <- D106_wis # Create new dataframe 
D106new$high_low <- rep.int(dummy, nrow(D106new)/2) # Add extra column delineating high and low alleles
D106new <- gather(D106new, key = "loci", value = "genotypes",
                      colnames(D106new[,-1])) # Gather data
D106new$high_low <- rep.int(dummy, nrow(D106new)/2) # Reallocate high and low designations
D106new <- D106new[,-c(2)] # Remove loci column
D106new <- D106new[-c(25:48),] # Remove doubles? Not sure where they came from
D106new_wide <- spread(D106new, high_low, genotypes, fill = 0) # Spread data
names(D106new_wide) <- c("Sample_ID", "D106_high", "D106_low") # Rename column


# D113_wis
D113_wis[(nrow(D113_wis)+1),] <- c("PWO10", "300")
D113_wis[(nrow(D113_wis)+1),] <- c("PWO3", "300")
D113_wis[(nrow(D113_wis)+1),] <- c("PWO4", "296")
D113_wis[(nrow(D113_wis)+1),] <- c("PWO7", "296")
D113_wis[(nrow(D113_wis)+1),] <- c("PWO8", "296")
# Order data
D113_wis <- D113_wis[order(D113_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D113new <- D113_wis # Create new dataframe 
D113new$high_low <- rep.int(dummy, nrow(D113new)/2) # Add extra column delineating high and low alleles
D113new <- gather(D113new, key = "loci", value = "genotypes",
                      colnames(D113new[,-1])) # Gather data
D113new$high_low <- rep.int(dummy, nrow(D113new)/2) # Reallocate high and low designations
D113new <- D113new[,-c(2)] # Remove loci column
D113new <- D113new[-c(25:48),] # Remove doubles? Not sure where they came from
D113new_wide <- spread(D113new, high_low, genotypes, fill = 0) # Spread data
names(D113new_wide) <- c("Sample_ID", "D113_high", "D113_low") # Rename column


# D114_wis
D114_wis[(nrow(D114_wis)+1),] <- c("PWO5", "244")
# Order data
D114_wis <- D114_wis[order(D114_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D114new <- D114_wis # Create new dataframe 
D114new$high_low <- rep.int(dummy, nrow(D114new)/2) # Add extra column delineating high and low alleles
D114new <- gather(D114new, key = "loci", value = "genotypes",
                      colnames(D114new[,-1])) # Gather data
D114new$high_low <- rep.int(dummy, nrow(D114new)/2) # Reallocate high and low designations
D114new <- D114new[,-c(2)] # Remove loci column
D114new <- D114new[-c(25:48),] # Remove doubles? Not sure where they came from
D114new_wide <- spread(D114new, high_low, genotypes, fill = 0) # Spread data
names(D114new_wide) <- c("Sample_ID", "D114_high", "D114_low") # Rename column


# D119_wis
D119_wis[(nrow(D119_wis)+1),] <- c("PWO10", "323")
D119_wis[(nrow(D119_wis)+1),] <- c("PWO3", "332")
# Order data
D119_wis <- D119_wis[order(D119_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D119new <- D119_wis # Create new dataframe 
D119new$high_low <- rep.int(dummy, nrow(D119new)/2) # Add extra column delineating high and low alleles
D119new <- gather(D119new, key = "loci", value = "genotypes",
                      colnames(D119new[,-1])) # Gather data
D119new$high_low <- rep.int(dummy, nrow(D119new)/2) # Reallocate high and low designations
D119new <- D119new[,-c(2)] # Remove loci column
D119new <- D119new[-c(25:48),] # Remove doubles? Not sure where they came from
D119new_wide <- spread(D119new, high_low, genotypes, fill = 0) # Spread data
names(D119new_wide) <- c("Sample_ID", "D119_high", "D119_low") # Rename column


# D125_wis
D125_wis[(nrow(D125_wis)+1),] <- c("PWO7", "278")
# Order data
D125_wis <- D125_wis[order(D125_wis$Sample_ID),]
# Spread data
dummy <- c("high", "low") # Create dummy vector
D125new <- D125_wis # Create new dataframe 
D125new$high_low <- rep.int(dummy, nrow(D125new)/2) # Add extra column delineating high and low alleles
D125new <- gather(D125new, key = "loci", value = "genotypes",
                      colnames(D125new[,-1])) # Gather data
D125new$high_low <- rep.int(dummy, nrow(D125new)/2) # Reallocate high and low designations
D125new <- D125new[,-c(2)] # Remove loci column
D125new <- D125new[-c(25:48),] # Remove doubles? Not sure where they came from
D125new_wide <- spread(D125new, high_low, genotypes, fill = 0) # Spread data
names(D125new_wide) <- c("Sample_ID", "D125_high", "D125_low") # Rename column
```


# Merge loci genotypes together 
```{r}
# Merge genos of a few and edit before adding more
genos <- merge(A103_new_wide, A115_new_wide, all= T) 
genos <- merge(genos, A120_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C1_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C6_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C105_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C125_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D4_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D10_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D106_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D113_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D114_new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D119_new_wide, by="Sample_ID", all=T)
original_genos <- merge(genos, D125_new_wide, by="Sample_ID", all=T)
original_genos[is.na(original_genos)] <- 0
View(original_genos)


genos <- merge(A103new_wide, A115new_wide, by="Sample_ID", all=T)
genos <- merge(genos, A120new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C1new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C6new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C105new_wide, by="Sample_ID", all=T)
genos <- merge(genos, C125new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D4new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D10new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D106new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D113new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D114new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D119new_wide, by="Sample_ID", all=T)
genos <- merge(genos, D125new_wide, by="Sample_ID", all=T)
View(genos)
genos[is.na(genos)] <- 0
Wisconsin_genos <- genos
```


# Edit original genos and Wisconsin genos and merge
```{r}
# Remove duplicate Chip6
original_genos <- original_genos[-c(63),]
# Merge oringal genos and Wisconsin genos
master_genos <- merge(original_genos, Wisconsin_genos, all=T)
# Change names 
master_genos$Sample_ID <- gsub("Chip6", "Chip-06", master_genos$Sample_ID)
master_genos$Sample_ID <- gsub("Chip19", "Chip-19", master_genos$Sample_ID)
# Order master list
master_genos <- master_genos[order(master_genos$Sample_ID),]
```


# Add new sample IDs to master list
```{r}
# Allegheny
ALL <- master_genos[-c(1:14),]
ALL <- ALL[-c(21:110),]
ALL <- ALL[-c(23:65),]
View(ALL)
ALL$New_ID <- 1:nrow(ALL) # Create New_ID column
ALL <- ALL[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
ALLvec <- c("ALL1", "ALL2","ALL3", "ALL4", "ALL5", "ALL6", "ALL7", "ALL8", "ALL9", "ALL10", "ALL11", "ALL12", "ALL13", "ALL14", "ALL15", "ALL16", "ALL17", "ALL18", "ALL19", "ALL20", "ALL21", "ALL22") # Create a vector of new sample IDs
ALL$New_ID <- rep.int(ALLvec, nrow(ALL)/22) # Allocate new IDs

# Chippewa
CHIP <- master_genos[-c(1:42),]
CHIP <- CHIP[-c(22:127),]
View(CHIP)
CHIP$New_ID <- 1:nrow(CHIP) # Create New_ID column
CHIP <- CHIP[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
CHIPvec <- c("CHIP1", "CHIP2","CHIP3", "CHIP4", "CHIP5", "CHIP6", "CHIP7", "CHIP8", "CHIP9", "CHIP10", "CHIP11", "CHIP12", "CHIP13", "CHIP14", "CHIP15", "CHIP16", "CHIP17", "CHIP18", "CHIP19", "CHIP20", "CHIP21") # Create a vector of new sample IDs
CHIP$New_ID <- rep.int(CHIPvec, nrow(CHIP)/21) # CHIPocate new IDs

# Meramec
MER <- master_genos[-c(1:71),]
MER <- MER[-c(10:55),]
MER <- MER[-c(15:18),]
MER <- MER[-c(30:48),]
View(MER)
MER$New_ID <- 1:nrow(MER) # Create New_ID column
MER <- MER[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
MERvec <- c("MER1", "MER2","MER3", "MER4", "MER5", "MER6", "MER7", "MER8", "MER9", "MER10", "MER11", "MER12", "MER13", "MER14", "MER15", "MER16", "MER17", "MER18", "MER19", "MER20", "MER21", "MER22", "MER23", "MER24", "MER25", "MER26", "MER27", "MER28", "MER29") # Create a vector of new sample IDs
MER$New_ID <- rep.int(MERvec, nrow(MER)/29) # MERocate new IDs

# Mississippi
MISS <- master_genos[-c(1:12),]
MISS <- MISS[-c(3:51),]
MISS <- MISS[-c(7:9),]
MISS <- MISS[-c(8:16),]
MISS <- MISS[-c(52:98),]
View(MISS)
MISS$New_ID <- 1:nrow(MISS) # Create New_ID column
MISS <- MISS[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
MISSvec <- c("MISS1", "MISS2","MISS3", "MISS4", "MISS5", "MISS6", "MISS7", "MISS8", "MISS9", "MISS10", "MISS11", "MISS12", "MISS13", "MISS14", "MISS15", "MISS16", "MISS17", "MISS18", "MISS19", "MISS20", "MISS21", "MISS22", "MISS23", "MISS24", "MISS25", "MISS26", "MISS27", "MISS28", "MISS29", "MISS30", "MISS31","MISS32", "MISS33", "MISS34", "MISS35", "MISS36", "MISS37", "MISS38", "MISS39", "MISS40", "MISS41", "MISS42", "MISS43", "MISS44", "MISS45", "MISS46", "MISS47", "MISS48", "MISS49", "MISS50", "MISS51") # Create a vector of new sample IDs
MISS$New_ID <- rep.int(MISSvec, nrow(MISS)/51) # MISSocate new IDs


# Ohio
OH <- master_genos[-c(1:69),]
OH <- OH[-c(2:99),]
View(OH)
OH$New_ID <- 1:nrow(OH) # Create New_ID column
OH <- OH[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
OHvec <- c("OH1", "OH2") # Create a vector of new sample IDs
OH$New_ID <- rep.int(OHvec, nrow(OH)/2) # Allocate new IDs

# Tippecanoe
TIPP <- master_genos[-c(13:34),]
TIPP <- TIPP[-c(17:46),]
TIPP <- TIPP[-c(18:108),]
TIPP <- TIPP[-c(20:26),]
View(TIPP)
TIPP$New_ID <- 1:nrow(TIPP) # Create New_ID column
TIPP <- TIPP[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
TIPPvec <- c("TIPP1", "TIPP2","TIPP3", "TIPP4", "TIPP5", "TIPP6", "TIPP7", "TIPP8", "TIPP9", "TIPP10", "TIPP11", "TIPP12", "TIPP13", "TIPP14", "TIPP15", "TIPP16", "TIPP17", "TIPP18", "TIPP19") # Create a vector of new sample IDs
TIPP$New_ID <- rep.int(TIPPvec, nrow(TIPP)/19) # TIPPocate new IDs

# Tennessee
TN <- master_genos[-c(1:38),]
TN <- TN[-c(5:95),]
TN <- TN[-c(7:33),]
TN <- TN[-c(9:13),]
View(TN)
TN$New_ID <- 1:nrow(TN) # Create New_ID column
TN <- TN[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
TNvec <- c("TN1", "TN2", "TN3", "TN4", "TN5", "TN6", "TN7", "TN8") # Create a vector of new sample IDs
TN$New_ID <- rep.int(TNvec, nrow(TN)/8) # Allocate new IDs

# Wisconsin
WIS <- master_genos[-c(1:67),] # Trim dataset to only WIS samples
WIS <- WIS[-c(2:64),]
WIS <- WIS[-c(4:20),]
WIS <- WIS[-c(14:17),]
WIS <- WIS[-c(18),]
View(WIS)
WIS$New_ID <- 1:nrow(WIS) # Create New_ID column
WIS <- WIS[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)] # Reorder columns
WISvec <- c("WIS1", "WIS2","WIS3", "WIS4", "WIS5", "WIS6", "WIS7", "WIS8", "WIS9", "WIS10", "WIS11", "WIS12", "WIS13", "WIS14", "WIS15", "WIS16", "WIS17") # Create a vector of new sample IDs
WIS$New_ID <- rep.int(WISvec, nrow(WIS)/17) # WISocate new IDs
```


# Merge datasets with new sample IDs
```{r}
genos <- merge(ALL, CHIP, all= T) 
genos <- merge(genos, MER, all=T)
genos <- merge(genos, MISS, all=T)
genos <- merge(genos, OH, all=T)
genos <- merge(genos, TIPP, all=T)
genos <- merge(genos, TN, all=T)
newID_genos <- merge(genos, WIS, all=T)

View(newID_genos)
newID_genos <- newID_genos[order(newID_genos$New_ID),]

names(newID_genos) <- c("Sample_ID", "New_ID", "A103", "", "A115", "", "A120", "", "C1", "", "C6", "", "C105", "", "C125", "", "D4", "", "D10", "", "D106", "", "D113", "", "D114", "", "D119", "", "D125", "")

write.csv(newID_genos, "Master_with_Sample_ID.csv")

NewID <- newID_genos[,-c(1)]
names(NewID) <- c("New_ID", "A103", "", "A115", "", "A120", "", "C1", "", "C6", "", "C105", "", "C125", "", "D4", "", "D10", "", "D106", "", "D113", "", "D114", "", "D119", "", "D125", "")

write.csv(NewID, "Master_with_New_ID.csv")
```


# Edit master (QC from GeneMarker)
```{r}
# A103
example <- newID_genos # Create new dataframe
example[106,4] <- 242 # 244 to 242 - INHS-16244

# A115
example2 <- example
example2[125,6] <- 346 # 285 to 346 - WV1
example2[40,5:6] <- 0 # 285 to 0 - Chip-06

# A120
example12 <- example11
example12[102,7:8] <- 226 # - MS35 
example12[154,7] <- 222 # 0 to 222 - PWO6
example12[154,8] <- 255 # 0 to 222 - PWO6
example12[155,7] <- 214 # 0 to 222 - PWO7
example12[155,8] <- 226 # 0 to 222 - PWO7

#C1
example3 <- example2
example3[20,9] <- 339 # 335 to 339 - ALL15
example3[73,9:10] <- 366 # 0 to 366 - A1
example3[152,9] <- 289 # 290 to 289 - UAUC3157
example3[39,10] <- 358 # 318 to 358 - Chip-05
example3[29,9] <- 335 # 331 to 335 - Chip-15
example3[31,9] <- 335 # 331 to 335 - Chip-17
example3[167,10] <- 397 # 335 to 397 - PW03
example3[7,9] <- 382 # 378 to 382 - ALL4

#C6
example4 <- example3
example4[53,11] <- 226 # 222 to 226 - PMC-3
example4[106,11:12] <- 0 #  0s - INHS-16244

#C105
example5 <- example4
example5[105,13] <- 269 # 265 to 269 - MS38
# Ran some reamps because there were conflicting genotype calls. Figured out samples were added to the wrong Genemarker file. This section is designed to fix the errors.
example13 <- example12
example13[97,13] <- 269 # reamp showed that 0 is 269 - MS30
example13[97,14] <- 291 # reamp showed that 0 is 291 - MS30
example13[100,13] <- 280 # reamp showed that 0 is 280 - MS33
example13[100,14] <- 310 # reamp showed that 0 is 310 - MS33
example13[101,13] <- 276 # reamp showed that 0 is 276 - MS34
example13[101,14] <- 315 # reamp showed that 0 is 315 - MS34
example13[103,13] <- 287 # reamp showed that 0 is 287 - MS36
example13[103,14] <- 315 # reamp showed that 0 is 287 - MS36
example13[111,13] <- 276 # reamp showed that 0 is 276 - MS42
example13[111,14] <- 280 # reamp showed that 0 is 280 - MS42
example13[49,13] <- 283 # reamp showed that 0 is 283 - PBH-5A
example13[49,14] <- 291 # reamp showed that 0 is 291 - PBH-5A

#C125
example6 <- example5
example6[110,15:16] <- 0 # 0s - MS41
example6[91,15:16] <- 0 # 0s - MS26
example6[45,15:16] <- 0 # 0s - PBH1A
example6[47,15:16] <- 0 # 0s - PBH3A

#D4
example7 <- example6
example7[144,18] <- 259 # 257 to 259 - 238-1
example7[39,17:18] <- 0 # 0s - Chip-05
# Ran some reamps because there were conflicting genotype calls. Figured out samples were added to the wrong Genemarker file. This section is designed to fix the errors.
example14 <- example13
example14[110,17] <- 266 # reamp showed that 0 is 266 - MS41
example14[110,18] <- 277 # reamp showed that 0 is 266 - MS41
example14[80,17] <- 270 # reamp showed that 0 is 270 - MS17
example14[80,18] <- 305 # reamp showed that 0 is 305 - MS17
example14[90,17:18] <- 317 # reamp showed that 0 is 317 - MS25
example14[115,17:18] <- 305 # reamp showed that 0 is 305 - MS6
example14[116,17] <- 305 # reamp showed that 0 is 305 - MS7
example14[116,18] <- 317 # reamp showed that 0 is 305 - MS7
example14[48,17] <- 277 # reamp showed that 0 is 277 - PBH-4A
example14[48,18] <- 309 # reamp showed that 0 is 277 - PBH-4A

#D10
example8 <- example7
example8[117,19:20] <- 0 # 0s - INHS-22893

#D106
example9 <- example8
example9[98,21] <- 276 # 280 to 276 - MS31

#D114
example10 <- example9
example10[106,25:26] <- 0 # 0 - INHS-16244

#D119
example11 <- example10
example11[134,27] <- 302 # 0 to 302 - INHS-3531
example11[134,27] <- 310 # 0 to 310 - INHS-3531
```

# Write csv file from altered genotype dataset 1/23/2018
```{r}
# Write CSV file
names(example14) <- c("Sample_ID", "New_ID", "A103", "", "A115", "", "A120", "", "C1", "", "C6", "", "C105", "", "C125", "", "D4", "", "D10", "", "D106", "", "D113", "", "D114", "", "D119", "", "D125", "")
write.csv(example14, "Master_with_Sample_ID_reamps.csv")

# Write csv file for GenAlex
genv1 <- example14
genv1 <- genv1[,-c(1)]
genv1$Pop <- 1:nrow(genv1) # Create New_ID column
genv1 <- genv1[c(1,30,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29)]
genv1[1:22,2] <- "1"
genv1[23:43,2] <- "2"
genv1[44:72,2] <- "3"
genv1[73:123,2] <- "4"
genv1[124:125,2] <- "5"
genv1[126:144,2] <- "6"
genv1[145:152,2] <- "7"
genv1[153:169,2] <- "8"
names(genv1) <- c("Individual", "Pop", "A103", "", "A115", "", "A120", "", "C1", "", "C6", "", "C105", "", "C125", "", "D4", "", "D10", "", "D106", "", "D113", "", "D114", "", "D119", "", "D125", "")

write.csv(genv1, "GenAlex.csv")
# In excel add two rows above microsatellite headings with information about number of loci, number of individuals, number of sample sites, and number of individuals at each sampling site.

# Write csv file for Microchecker
microchecker1 <- genv1[,-c(2)]
names(microchecker1) <- c("Sample no.", "A103", "", "A115", "", "A120", "", "C1", "", "C6", "", "C105", "", "C125", "", "D4", "", "D10", "", "D106", "", "D113", "", "D114", "", "D119", "", "D125", "")

write.csv(microchecker1, "Microchecker.csv")

####################################################
# Remove pigtoe samples!!
pt <- read.table("GenAlex_woOH_woD113_1.30.18.csv", sep = ",", na.strings = c("", "NA"))
v1 <- pt[-c(48:50),] # PBH1A, PBH2A, PBH3A are pigtoe samples not sheepnose

write.csv(v1, "Genos_woPigtoe.csv")
```



















